\unnumberedsection{Introduction}

\par In this work, I will address the negative obscure [destructive] side of the feminine, which unfortunately correspond in these decaying current days to a great amount of existing women.
I will not address their divine and [celestial] side, which is equally true, but only their negative aspect, which must be defeated so that a woman voluntarily hands us over the Heaven's key.
It's only by matter of focus that only this side will be criticized.

\par Whoever opens this book must always take into account the fact that I am describing a very specific type of woman - the love-cheating devious woman - and that the pointed out characteristics are, most of the times, unconscious.
The indicators of this unconsciousness are the strong female reactions of resistance against all attempts to communicate them this reality: indignation, surprise, anger, or [summary?] denial.
I am not [busying myself] with sincere women in this book, and all that I explain, detail, and describe here is nothing more than an hypothesis.
It is not an absolute immutable truth that cannot be questioned and of which one must not doubt.
I describe here the feminine form [embodied] by human traits belonging to both genders.
If I do not occupy myself with the masculine form embodied by such traits, it is simply because this is not the goal of this book and also because many books have been written about it.
I hope that I will not have to repeat this a million times. I am tired of stressing these points.

 The ability to deal with the obscure side of women consists of the assimilation of a set of knowledge that almost constitute a science.
 I disagree with thinkers who consider them incomprehensible.
 
 Women are deliciously terrible, two-faced beings who alleviate our pains, but, at the same time, make us suffer terribly.
 
 Sometimes, they torment us with their contradictory games and inconsistencies, driving us mad.
 When we defeat them, they gift us with the wonderful secrets and delights that they [reserve] to [elected men].
 They are not inherently bad, they are only humans, like us.
 
As I have seen many men suffering in the hands of these delicious creatures, I have decided to share the knowledge that I have acquired in tough experiences.

When I was young, I did not understand why some philosophers and writers say that we need to detach from women.
I would consider them unfair and would disagree.
Today I totally understand them and agree with much of what Nietzsche, Schopenhauer, Kant, Eliphas Lévi, and other wise men said.
The admoestations of Church in Medieval Age, of Alcorao, of Bible, and other sacred books about these simultaneously wonderful and evil beings are not for free.

The game of passion is a battle of feelings in which a woman try to win by using a man's affective and sexual deficiencies.
Her intention is to win our heart so that, this way, they can benefit from the subservience stemming from the state of being in love.

The guidelines that I point out are generally applicable to stable relationships of genders: to courtship, to dating, and to marriage,  among other "modes" (and, therefore, are intended only for adults).
The information was gathered along with works of respectable authors and from contact, observation, and personal experience.
I cannot say a thing about what does not pertain to a context experienced by me, because I obviously do not know all the women on the Earth.
In no way do I deny that the superior and the inferior coexist and that there exists a wonderful sublime divine spectrum in women.
However, I suspect that there are not many, in these decaying times, that seek to fuse with their positive superior side.
This side seems to have been banned into the unconscious[1].
Many women seem to identify themselves with their synyster side, with the dark side clearly pointed out in myths and this was what has drawn my attention.
We can say that the fault for our suffering is only ours and the fault for them being this way is only theirs.
There could be other ways if we were different...
Unfortunately, human kind prefers the evil one.
Our share of responsibility for suffering in their hands consists of our debility in giving ourselves to [desenfreio] of our animalistic passions and to sentimentality.
Thus, we neither have nor must have anything against women, but rather against ourselves: against our naivety, our ignorance in not seeing reality, and in fooling ourselves.

Basically, I have dedicated myself to describe female strategies to ludibriate a man in the field of love, while chaining him, the mistakes that we usually make, and means by which we can emotionally defend ourselves (in the cases when this defense is legitimate and justified).
I hope that I have not shocked the reader for having, like Machiavelli, addressed only the real things and not the ideal things.
The reality of what we usually understand by love is not too pretty and usually differs from what we would like it to be.

My intentions while making this work were:
1) provide a model that made understandable the seemingly contradictory female behavior;
2) provide a set of knowledge that allowed men to protect themselves from emotional abuse and, thus, that had the effect of minimizing gender conflicts;
3) dismantle tricks, ruses, and [espertezas] in love.
It was not my intention to simply "demean" this or that gender.
I do not demean women: I judge and reprove their negative attitudes in the field of love for knowing that, in the war of love, mercy seems not to exist, unfortunately.
Regarding their positive side, I will not address it in this book, in spite of it existing and being very important, simply because it would digress us from the focus of our interest.
I have not created women, I only describe them as they seem to me, without masks or evasives.
The complex, confuse female world needs to be talked about in a crude, straightforward, realistic, and objective way in order to be understood.
However, the reader must remember that this is just a personal viewpoint and nothing more.
It is not a finished, unquestionable truth which cannot be doubted; they are ideas exposed to discussion for continuous improvement and not dogmae.
The several discussions raised by previous editions allowed a great progress and showed ways for [aprofundamento].
Criticism is always welcomed.

There are no arguments in this book in favor of negative sentimentalty.
We argue against passion.

I hope that people do not mistake me for a mere extremistic dogmatic machist person.
I also do not recommend resentment, promiscuity, or polygamy.
A real man does not need to cheat, he does not need many women, because he is able to conquer a woman who completes him, to get from her everything he needs to be loyal.
Promiscuous men seem to me weak, unable to bear the torments of his only wife without resorting to other lovers as [muletas]
If you need many women, this may be suggesting that you are unable to get satisfaction from one only.
A superior male transforms his partner into a wife, lover, and girlfriend at the same time, not giving her a way out other than to become a sincere complete perfect super-woman, or decide to end the relationship

This is not a seduction manual, but rather a philosophical reflection about coexistance and the power that an (adult) man has over himself.
It is a [bem humorado] essay, but which sometimes allows for a rant, about female behavior and about masculine self-power.
If I sometimes provide strategic information about conquer, I do it simply to help men who have difficulty in getting or keeping an adequate partner, since women often have an inversed value system that make them prefer the worst men, a fact that harms them.

Ultimately, we suffer by our own fault and not by their fault.
What weakens, destroys, subjects, and anihilates us are our own desires and feelings.
A woman simply takes advantage by using them as tools to reach us.
Thus, the solution is to fight ourselves, by psychically dissolving ourselves through the death of our ego, instead of trying to force women to fit the patterns that we would like.
I am radically opposed to each and every form of mental manipulation of the other.
Instead of manipulating the other, it is better for us to learn to manipulate ourselves.

People from both genders behave in a mechanic conditioned way, with only very few being able to rebel against themselves to the point of totally escaping the animal patterns of behavior.
Thus, it seems there are not many women on the Earth who appear to distant from the behavioral profile here described, unfortunately.