\section{The steps to the enchant work of refractory and [arredia] women}

\par To good men who have not yet found an appropriate partner and do not know what to do, I will give now a few tips. I do it only to help good men, since women seem to prefer bad boys. However, it must be clear that this is not a book about seduction. These tips are only so that unprivileged men can compete with the preferred men and overcome them in the [acirrada] competition for females.

\par The enchant work has three important steps. In the first step, we have not had any contact with a woman who we want to own. In the second step, we have made a contact but intentions are not revealed yet. In the third step, the intentions have been revealed. Seduction of strangers belong to the first step. Friendship belongs to the second one. All relationships that start after we declare what we want belong to the third one. We will [let us?] study the first one.

\par The [main] guideline that leads all enchant work is the narrowing of intimacy mixed with indifference and disinterest.

\par Fixate your gaze at any woman who is pretty, full of herself, snobbing, and less smart. You will see her looking away.
What will be happening in these moments is a rejection, a refusal stemming from thoughts in her annoying hoe's brain. What is she thinking about?  It is easy to guess: that you are only another idiot like any other, that you do not have anything interesting because, if this was not the case, you would be with a "potranca" by your side and would be despising all other women.  Therefore, it is a waste of time to keep flirting like this, because the ladies who will reciprocate it are only the very "ugly" and annoying women who feel rejected, and not the best.  Only desperate women accept chasing men.
 
\par The most desirable women keep their guard continously up, and [...]. What you must do is to make them lower their guard by their own will. To get her to open up, you must convey rejection or indifference. You must find a silent way to tell her, as if you do not want to do that, that she is uninteresting and that you do not notice her. For that, it is enough that you ignore her presence, avoiding to look at her body and face. But this is not all.
 
\par Once you have proceded this way, you will have bothered her, as you can note by her gestures and movements (...). You will begin to be observed, with her peripherial or focal vision.
 
\par Surprise her by greeting her in a bold fearless way, before there is time to think and while staring at her eyes in an extremely serious way, but yet with some indifference. If you catch her looking at you, she will have no other way other than to reciprocate your ... Contact will have been established. Next, if you want to start a conversation, speak in a commanding tone, with a low-pitched voice, while always paying attention to emotional ... If you notice an opening, make advances, but take care not to go beyond or [...] from allowed. If her walls are still up, that is, if the woman is still closed, not giving any open signal for an advance, disagree with her opinions, provoke a discussion but do not end it. Then give her your phone number or email to continue it, with a deadline.
 
\par In extreme cases, it is necessary to impress her very much by \enquote{horrifying} her in a calculating way. Do not go on \enquote{horrifying} her in any way: impress her in the correct way, so that the result is not a disaster. A good way to mark her imagination so that she remains thinking about you for some time is to declare yourself a sexist person (an enlightened, self-aware, peaceful, and protective one, of course), because your rivals will always pretend to be feminists to please her. What matters here is to stand out as a different, secure man, who is not afraid of showing his convictions and who does not need anyone. About this subtlety, Eliphas Lévi tells us the following:

\begin{displayquote}
	A man who wants to make himself loved (we attribute to a man only all these illegitimate maneuvers, assuming that a woman does not need them) must, at a first time, ingratiate himself and make any impression on the imagination of the person who is the object of his desire. He must ...
\end{displayquote}
 
\par Lévi refers to a small (and therefore harmless) horrification. His explanation helps us understand why females feel so attracted to certain evil and perverse men. These men impress them strongly, much more than certain good men. To trump them, you must master this skill and use it for good, in the correct way. If you use it for evil, you will attract bad consequences to yourself.
 
\par Some women usually show themselves as open at first, but, after contact, they stay silent to disconcert us, while they observe how we will get out of this embarrassing situation and having fun at our expense. In this case, be short and sweet with your comments, taking the initiative to end the conversation before you look stupid. If you are on the phone, take the initiative to hang up; if you are talking face to face, take the initiative to end the conversation and leave without looking back. Postpone the advances to another day, teaching her a good lesson. This will impress her. Usually, in the next following contacts, the lesson has effect and makes her more loving... Do not make advances while her guard is up.
 
\par The conquer of a lady has steps that go since the moment that we do not know her yet, to the steps in which we have to conquer her again.