\section{About a woman's desire}

\par Female desire is something very controversial and disconcerting. Much confusion reigns about it. This is mainly due to the opposition between what is conscious and what is unconscious. One cannot know the factors that ... through questions, interviews, etc., because we will be fooled. You must know that almost everything that we hear a devious woman say about what she looks for in a relationship is a lie, and, moreover, is usually precisely the opposite of what they really desire. I will now expose what they try to hide and never admit.
  
\par Human sexuality is similar to that of savage horses, zebras, .... Females spontaneously move to the territory of a stud, who stays next to the best sources of food and water (material resources), and offer him their sex as he pleases. The other, secondary males are forced to wander in bandos made only of individuals of the male gender, remaining without mating for years straighy, until they can replace some old stud. Females do not rivalize against themselves and accept the infidelity of the stud without a problem (as it happens with female fans of any famous artist, gangster, billionaire, or politician). The stud can have sex with any ... of his without a problem, as long as he is able to scare beasts and chasing secondary males away. In other words: men who are considered "alpha males" behave like savage studs, and women who chase them behave like their females. On the other hand, men who have been excluded by the female selective criterion are like rejected horses who never mate. Something very similar happens among lions, among gorillas, and other animals.
  
\par For being the complement and polar opposite of men, women have an inverse psychic structure.
  
\par We want as much sex as possible and we try to have sex as long as we have strength, until our last moment. For us, sex comes in the first place and love, in second. For them, the opposite occurs: love come first. But understand this well: most of the time, they do not want to give love, they want only to receive it, while they give us in return only the smallest necessary amount to keep us tied up through desire, through sentimentality, and through passion. They have a double desire. They desire the servitude of weak men and the protection of strong men. They want to dominate debil and needy men to exploit them as husbands ... of her offspring, at the same time they dream about having the affection of insensitive men who have harems and stand out in the male hierarchy. Weak men, when tied up, receive sex, affection, and love in minimal amounts, only enough to be kept tied.
  
\par They do not love us by mere automatic reciprocation of our love, that is, simply because we love them or desire them. They desire our attractive traits and not the person who we are in and of itself. This is explained by the fact that their needs are way beyond mating: they need to create and protect their offspring. Therefore, they do not miss males themselves, but only male behaviors in utilitarian contexts. We, on the other hand, love them in themselves, that is, in a direct way, because our existential goal is to mate. We want to pass our genes rather than other men's genes. We love them in body, in a direct way. We are loved indirectly, in terms of functionality and utility. We are not missed outside of an utilitarian context.

\par Male existential goal is to mate, fecundate, and guarantee the transmission of genetic inheritance against rival males. Female existential goal is to foster her offspring...