\section{How to be fascinating before a woman's eyes}

\par To start off, a man must have a real attractiveness, and not only pretend to have it. If you think you will be able to fuck everyone by only pretending, you can throw your brain into the toilet, because you are utterly mistaken. A woman will observe you and will notice your pretense and your weaknesses from your behavior. Then, she will pretend to be fooled by you and will screw you up somehow. You will cry, and do not bother mailing me because I will tell you to go straight to hell.

[...]

\par If you are shy, fearful, sentimental, sensitive, needy, or retiring, and want to be like this forever, stubbornly refusing to change, give up because women are not for you. Renounce your masculinity and forget about women because fragility is a feminine attribute, not a masculine one. Of course, we, males, have limitations and weaknesses, but women do not want to see it. They are intolerant to our weaknesses and fragility, even though they say otherwise.

\par A first attribute that drive females crazy is the masculine ability to make money. This happens because they have an ancestral instinct to prostitution since the paleolithic and want to give sex to men who have the most material resources, just like female of other mammals do. Prostitution is the oldest female profession and we must not have prejudice against prostitutes. Of course, no devious woman will admit it and will even simulate outrage, but observation will reveal it with mathematical precision. Notice that the richest males stay with women who other males would like to have. Verify this fact and then conclude it by yourself if I am lying or not about it. But make no mistake: if you only have money and nothing else, you will also be cheated on because she will not feel fulfilled. If you only want to have fun without commitment, there will be no problem, but do not try to marry her because you will be used only for being a material resources provider, and other guys will be taking her to the love hotel.

\par A second attractive attribute is indifference. If you keep hitting on women like desperate, the only one who will do is to make them believe that you are inept and unskillful at courtship, a mere chaser. A fascinating man does not attack them, does not hit on them, and does not mess around with them. He simply exists with his attractiveness and observes them as though he is not observing them, keeping his aloofness while they go crazy. He seeks and builds relationships without pretense.

\par If you are already seeing a delicious woman regularly, a good way to reach indifference is to work on the death of the egos involved in passion. When your partner begins playing games, tests, and psychological torture sessions, keep your mind off this useless bits and you will see how she will be chasing you like crazy.

\par Men who keep catcalling women in the street, chasing them everywhere or groping them, are nothing more than incompetent dumbasses. It is because of them that it is so hard to conquer the hottest, who think men are all the same.

\par A third attribute is to be sociable. Mind you: you must be indifferent yet friendly. If you stay retired, hatching eggs in your house and waiting for a beautiful creature to fall from the sky with her vagina open upon your head, you will grow old [abated]. You must meet many women, be their true friend, and gradually become more and more intimate. To make her crazy to give you sex, you must keep talking to her about herself, while you get to understand her more and more. Soon she will be telling your her intimacies. Do not betray her.

\par Women, just like men, have an enormous need to be understood without understanding the other. But do not think that this means that we must do everything that they want. When a man really understands female psyche, he knows all of its tricks and tests. He knows that, if he is submissive, he will be deemed a poor thing and that he needs to become better than her in all regards to be attractive.

\par A fourth attribute is intelligence. A stupid guy is a good-for-nothing. But do not go around being a smarty pants, because you will also become annoying. You must watch your mouth, be profound in your speech, and have her life in the center of the conversations, as if you knew her better than herself. Try to study, to have at least a reasonable degree of instruction, so that her female unconscious deem you superior to other hominids.

\par A fifth attribute is to stand out. Any male who stands out in a group is desired by the females of the lot. Lecturers, for instance, when they are good and make an impression, almost always fuck some \enquote{skanks} of their audience.