\section{Cares to be taken when we deal with devious women who try to cheat in love}

\par Obs. 1. Never use this knowledge for evil (seducing many women at the same time, fooling virgin girls, seducing underages, etc.). Do not try to be the "alpha male" stud who fucks everyone, because the destiny of such a man is to be killed, get STD, or become impotent in all senses, including sexually, and to be replaced by ascending beta males

\par Obs. 2. This information is only intended to help well-intended men who are unprivileged in the tiring competition for females, and not to encourage male promiscuity. If you use it the wrong way, it will be your fault.

\begin{enumerate}
  \item Never try to kiss her if she looks away while you get closer to her.
  \item Excite her imagination by making her constantly think about you, preferably as a man completely different from other men.
  \item Strongly impress her without bragging off
  \item Be mysterious
  \item Hide your sexual intention until the [...]
  \item Steer the conversation in the direction of her emotional problems and not yours. Do not talk about stupid things
  \item Wait patiently that ...
  \item Be regular in the frequency of your conversations
  \item Let her define the duration of a conversation and of the intervals between one conversation and another.
  \item Never show sexual hurry or urgency
  \item Let her talk about sex, if she wants to, and show great understanding about the matter
  \item Make her depend on your conversations.
  \item Agree with her many times but not always
  \item Do not monopolize the conversation. Let her talk as much as she wants to. You must only listen and ... the subjects in the way that interest you by encouraging her to talk so that she is not left without a subject
\end{enumerate}

\par Important: it is imperative to notice the kind and depth of the given openings so that you can make appropriate advances. A ... results in a failure.