\centering \large{\textbf{Warning!}}

\justifying \small

\par This book is free of charge. If you paid for it, you have been scammed.

\par There are no complements, other versions, or other authorized editions being commercialized. All versions which are not this present one are unauthorized, and have possibly been tampered with.

\par You ARE NOT ALLOWED to sell, edit, insert comments, insert images, extend, reduce, tamper with, plagiarize, or commercialize this book anywhere. No change of its content, language, or title is authorized.

\par Respect the author's rights.

\centering \large{\textbf{Disclaimer}}

\justifying \small

\begin{bfseries}
\par This work must be read under the perspective of humor and solidarity, never anger.

\par This book teach men the art of dismantling and neutralizing female tricks in love and how to protect themselves against the emotional dangers of passion, which cannot be mentioned as incentive or backing to any form of aggression.

\par Its critical, straightforward, ironic, and incisive tonality only reflects notes of defects, mistakes, and tricks, not be taken as support for any attempt to cause harm to human beings. It is one thing to dismantle the deeds of women who attack in love and criticize them in this field. It is a completely different thing to harm them.

\par The denounced, unmasked, and described ruses correspond to female expressions, mostly unconscious, of behavioral traits common to both genders. The outlined profile corresponds to a specific kind of woman: the one who is driven by sentimental selfishness. The author does not say anything about the percent incidence of such a profile in the female population of different countries.

\par The author is also not responsible for any misinterpretations, biased readings, inappropriate generalizations, or deliberate skewing that are made under any claim, or by misapplication of this knowledge. Those who skew it or misuse it will have to answer for their deeds on their own.
\end{bfseries}