\unnumberedsection{Introduction}

\par A lot has been written about the perfidy of men, and little has been written about the perfidy of women. Not denying at all the existence of a superior, wonderful, idyllic, and divine side of the feminine, nor the negative side of the masculine, I come now to try to supply that lack by clarifying a little what is missing.

\par There are two instances in a woman: one superior and another inferior. The superior side corresponds to the authentic Woman; the inferior side corresponds to the humanoid female animal. People are not used to talk about the evilness of the female animal, it is a taboo. Anyone who dares to point out the female cruelties and debilities is immediately labeled as a mere obsolete, misogynist, and sexist person. Unfortunately, women are currently in large part negatively polarized with respect to men, not always giving a voice to the superior and good side that exists within them. The truly sincere, who also exist, are lost in the crowd and cannot be found so easily, because devious women impersonate honest ones\footnotemark[1]. As women who are no use for marriage are dissimulated and swear their soul they are loyal, honest, and sincere, the little who would work in a serious and stable relationship cannot be spot without great difficulty. Women (and men) who are sincere for love were never abundant throughout history, but are nowadays in rapid extinction, quickly disappearing due to the decay and degeneration of our species\footnotemark[2].

\footnotetext[1]{I refer to honesty of feelings and not the number of sexual partners. A woman who's not satisfied with one man and want to have many partners cannot be accused of insincerity if she makes this clear \enquote{in the contract,} that is, from the beginning.}

%TODO "love decay" or "love decadence"? or maybe something else?
\footnotetext[2]{This love decay also affects, obviously, men, but it's expressed in a distinct way from that which interests us here.}

\par Women seem to me more prone than men to certain emotional obsessions: they are unpredictable, contradictory, change all the time, never know for certain what they want, want incompatible things, and not always orientate their behaviors logically\footnotemark[3]. Their hormonal oscillations, tendency to postnatal depression, body fragility, etc. are elements to be taken into consideration the moment we judge their actions, which invariably forces us to be indifferent to their cruelty and not to take them too seriously, forgiving them, under penalty of suffering a little if we do not. He who does not accept women as they are, pointlessly struggling against the inevitable, will lose his mind because sadness drags us along when we chase them. He who \enquote{chases} female inconsistency to try to revert it by force is already chained without realizing it.

\footnotetext[3]{However, the behavioral contradictions serve defensive goals (and sometimes offensive ones) when they paralyze a man's actions.}

\par An obsession that many women are prone to consists of obsessively desiring to be loved\footnotemark[4] without paying the corresponding price by giving love, certainty, and loyalty. It is a manipulative selfishness that does not consider the suffering caused onto the other, very similar, in this sense, to the insane selfishness in men who take sex from women by force\footnotemark[5] or pressure them to give in. Instead of complaining, it is better to forgive and accept, adapting ourselves to the real conditions that are offered us and not feeding any expectation out of reality.

\footnotetext[4]{The obsession with the continuity of male interest, which Francesco Alberoni describes. It's an instinctual and natural tendency, a mechanism of the unconscious for preservation and control, of which a woman can only be deemed guilty when she's passive before herself. Women who assimilate this instinct become virtuous, sincere, understanding, and true gems.}

\footnotetext[5]{This obscure side of men originates an ancestral resentment.}

\par I know many will be angry at me for having written truths about women that they try to hide at all costs. However, I tell the angry that I am helping them, because I expose behavioral traits that damage not only their partners and suitors, but also themselves. I point out the weaknesses of the feminine and of the masculine, as well as means by which ill-intended men can break women's resistance and defeat them, being evident that I am helping them to recognize and protect themselves against the nefarious effects of their own evilness. Moreover, I provide experience subsides for them to advise and orientate children, siblings, and other male relatives against the dangerous magnetism of passion. To critics, I suggest you refute my ideas instead of depreciating them.

\par I am a defender of monogamy, conjugal fidelity, and family. I have written this work for sincere men who are defeated in the war of passion and cannot master their relationship with their wives, girlfriends, companions and/or partners. My target audience are also strong men who do not fear the truth, weak men who want to strength up themselves, and brave men who do not want to waste their time being deceived. In short, I write for men who like to think by themselves, want to go beyond the deceiving games, and seek a realistic relationship based on bald truth, not on delusion, lies, deception, fraud, tricks, dreams, manipulation, and foolish romanticism. Only such men will do well by applying my knowledge. Those who attempt to apply it for selfish ends or with bad intentions, such as seducing to fool, becoming \enquote{alpha male} players, manipulate women, etc. will have the opposite of the desired effect. I do not write for immature people who do not distinguish criticism from anger, who do not want a stable relationship, who are looking for someone else to tell them what to do instead of thinking and deciding by themselves. I neither am nor wish to be a master of anyone; I am not looking for pupils, admirers, or followers. I look only for sincere and mature readers to question, in a sober and critic manner, the hegemonic beliefs and paradigms. If you are not any of these, close this book because the message is not for you.

\par Our purpose is to find out the true feelings and intentions of women, so that we do not waste our time with the insincere. Neither is our goal to attract indifferent women or let alone win their heart, but rather quickly identify and dismiss them. We assume we should not chase women who blow us off or reject us, nor should we waste time trying to make them attracted to us. It is faster and more efficient to find the less insincere.

\par I am not denying that males have a dangerous shadow\footnotemark[6], but the goal here is to describe the female shadow, and I will not deviate from this goal.

\footnotetext[6]{It's possible I go further on the male obscure side in the future, but I can't guarantee I will.}