\section{The Illogicality}

\par Between the passionate feelings\footnotemark[7] of a man and a woman there is a perpetual disagreement resulting from the fact that men who love are used as emotional slaves whereas insensible men are loved. It is an outlandish contradiction: women who complain about not being loved are precisely those who reject men who love them and prefer insensible sleazebags. This preference for swingers, scumbags, Don Juans, powerful men, famous men, leaders, etc. who do not fall in love and have many suitors and lovers makes realization of passionate love impossible. It is impossible that a person who adopts indifference as a criterion for electing their object of love to be happy due to the very contradictory nature of their choice. Choosing an insensible man as the ideal person to be happy in love is like electing, among many alternatives, a car as the ideal vehicle to cross the ocean. It is, at first sight, illogical. Not only illogical, it is harmful for women.

\footnotetext[7]{We must distinguish the inferior emotions of amorous passion from true love, which is a sublime form of feeling.}

\par The fact that they choose men who reject them as their object of love seems, at first, a proof that women are absurd, inconsistent, and illogical. However, this is a matter not resolved and agreed among all. I defend the hypothesis that such a behavior is illogical only on the surface or to a certain extent, hiding a principle entirely consistent with a manipulative, opportunistic, and selfish demeanor, but often unconscious: by offering love and sex to insensible men, women in reality do it moved by pride and thirst for power and for control\footnotemark[8]. In other words, they are absurd, unwise, and illogical only in certain aspects of the problem. They are cunning strategists. Insensible men invite them with the possibility of giving them power and prestige, since such men are those who in the short term stand out over good men in the wild fight for survival. This superiority is apparent because, in the end, you reap what you sow, but it is enough to fool women since they are often irrational\footnotemark[9], emotive, superficial, volatile, and easily affected by bad apples.

\footnotetext[8]{A predatory woman exerts control over a man through his passion.}

\par Polygamous, depraved, and promiscuous men excite a woman's curiosity and desire to dominate them by love. Curiosity makes her think, \enquote{If he has many women, he must have something interesting. What is it that he has to attract so many?} Pride will say, \enquote{Am I able to make him fall in love with me and crawl for me?} And greed will make her think, \enquote{If I dominate him by love, I will have a slave to serve me and I will be treated like a princess.} When this backfires and the war of passion is lost, then they complain and whine, blaming us and generalizing.

\footnotetext[9]{I'm not an adept of rationalism.}

\par Insensible, womanizing, aloof, and cruel men are considered superior to good, honest, loyal, and working men. Women, then, try to bend them over and dominate them as they greed the position and status that they can get compared to their female rivals, who also desire them. When this fails, because they are tough guys, women go on complaining. Lamentation is then externalized under the false appearance of love and romantic sensitivity, from where stems the wrong and common idea that all women are tender misunderstood beings who reciprocate love with love. In reality, mere emotional love is often repaid with indifference, aversion, and infidelity, whereas coldness, confidence, and leadership, when taking protective aspects, are repaid with attempts of subjugation by means of hot erotic tender love. The fact that it is precisely the worst males who have access to the most beautiful women is a very meaningful proof that there is no room for sincerity and goodness in the war of passion. Aesthetically disadvantaged women accept good men because they feel rejected due to little attractiveness. When we give them physical beauty, they quickly change.

\par We have concluded from the above that women's passionate love is born doomed to not actualize by the simple fact that the criterion used for election of its object is unavailability.

\par On the other hand, there is in this harmful selective criterion something really absurd. Observing women, we see some authentic illogicalities which are not apparent, pretended, or contrived: those resulting from the natural female proclivity to psychological confusion. These are involuntary unconscious illogicalities, denied at all costs and inexplicable for being governed by mental chaos. Such traits explain why an intense interest, attachment, and commitment to us suddenly vanishes without a warning and never comes back. The lack of logical sense makes the absurd of wanting to be loved by rascals equally understandable. These are insanities that even they cannot explain and it originates from a rupture between their strong instincts and their intellect.

\par Attempting to force women by means of argumentation to recognize their mistakes, to make logical decisions, to be transparent, to admit the dissimulation, etc. always have the opposite effect and violate their nature, compelling them to defend themselves. However obvious it can be the lack of internal logic in a badly-told lie, such a fact will never be admitted and the melodramatic appeals to convince will prevail, turning an argument into an infernal pandemonium of confusing ideas and insane feelings.

\par It will always be a complete waste of time to attempt to make one realize their own badness, the cruelty in their actions in love, and the reasons by which they often play unworthy of love. Arguments will always turn into fights, because the emotive mind has almost no objectivity to allow one to approach themselves in a reflective self-analysis. They will muddle many unrelated subjects chaotically, treating emotively and superficially all addressed points, not allowing an in-depth understanding of any of them. A hundred percent narcissists, such people are incapable of seeing themselves for what they are.

\par However, there are also pretended illogicalities, such as those that some women emulate when they want to make it seem as though they are not understanding something obvious, evident, notorious, and manifest. These will be addressed in the next chapter.

\par Finally, we conclude that we must achieve an internal state in which we simply forget about the problems and confusions women create to relentlessly try to involve us. Due to the fact of existing real illogicalities and pretended illogicalities, it follows that there is no other way than indifference. Trying to force women to reveal what they feel, to define their stance, to not lie, to not hide, to not manipulate, etc. can be very useful in certain desperate emergency situations, but it is still granting them importance and, thus, giving them power, strength, and energy. The ideal thing is, thus, complete neutrality, indifference towards what they feel for us or for others, towards the (un)truthfulness of what they say, and towards their fooling and manipulating attempts.