\section{The Annoying Provocations}

\par Let us now study the hysterical provocations carried out by some shrews and that confuse us so much.

\par It is not unusual for some men to be defied or have their wrath provoked by attitudes, behaviors, or words of their partners. Such provocations are tests intended to measure their self-control, degree of passion, and capacity to correctly react to difficult situations.

\par When mixed with anger or wrath, the feeling of passion acts as a brake against the destructive aggressive behaviors of a pissed-off male for having been provoked. Therefore, according to the degree of aggressiveness of your reaction, a woman will know whether you are too much or too little in love with her, and also whether you are impulsive or have self-control. If you lose your head and get mad, you will show that you cannot control yourself, and thus are a lower category male, incapable of keeping your nerve in tense situations to protect her if necessary. If you lash out, you will show that you are not very submissive, but, at the same time, that you cannot control yourself. In both cases, you will be demoted before a devious woman's eyes, who will feel superior to you. On the other hand, if you do nothing, you will be suggesting that you are passive, submissive, and equally uninteresting. What should you do then?

\par Such a situation is difficult, almost a dead end. It is another trap to test and measure masculine values. If we react aggressively to a provocation, we lose the game. If we passively accept the provocation, we also lose it. But there is a solution: \textit{calmly unmasking the provocation in the very moment in which it is happening}, calling out the fact before her eyes and to her in order to make her feel discovered and ashamed. Do not ever fall into her trap. Do not assault her, do not shout, and do not curse your partner in any way, ever! Under no circumstances must you physically hurt her. This attitude will make you lose your mind and meet defeat in the war of nerves that is being waged. She will come off as a helpless poor thing and you will be seen as the bad guy. This is exactly what devious shrews want and try to elicit.

\par When we denounce, without fighting or arguing, in a direct and clear manner, exactly what is happening, pointing out which ones are provoking attitudes, the reasons by which those are defying, etc., we render our partner powerless because we make her feel caught up red-handed.

\par The act of defying and provoking aims not only at testing us but also at manipulating situations in order to highlight the provoking person as the victim. Historically, females have always instrumentalized this role as a social weapon for dominance and gaining protection and favors. In some cases of self-defense against perverse men, the use of this strategy is fair, but not in all cases.

\par When we allow a woman to come off as a victim (without actually being one) before ourselves, before themselves, and before other people, we become morally indebted. Then, we feel an intense emotional need to flatter, to please, to chase, etc., in order to be \enquote{forgiven.} The curious thing is that when the manipulation is perfect, the one who seeks forgiveness is precisely the innocent, and the one who has the power to forgive is the guilty one. It is an ingenious trick of mental manipulation that inverts each one's position, and it is typical of hysterical shrews\footnotemark[30].

\footnotetext[30]{Putting it another way, a man is manipulated by his feelings of guilt, as Esther Vilar explained.}

\par The key for dealing with such hysterical ploys is to catch the provocation underway and denounce it immediately, without giving any room for arguments and, of course, without fighting. You must use a strong, confident, and serious tone of voice, but speak little, in a short, curt, and direct manner, while looking straight into her eyes. Then, be silent and get away from her until she ingratiates herself with you for reconciliation\footnotemark[31]. If she does not ingratiate, replace her with a better woman because you will not have lost a thing: shrews who are not ashamed even after being caught up red-handed are incorrigible.

\footnotetext[31]{The moment that takes place immediately after the reconciliation of a fight or a breakup is very appropriate for starting a new pattern of relationship based on distancing, coldness, dedication, protective leadership, intense eroticism, sincere affection, and consciously dosed and articulated impartiality.}

\par Do not be a chatterbox or verbose. He who keeps his words and conversations to the bare minimum protects himself against female provocations. Speech gives away our feelings, limitations, and weaknesses.

\par The more you argue with your partner, the more complicated everything gets, because female arguments in such cases are capricious and illogical. Instead of seeking clarity and understanding while arguing, they seek to alternately annoy us, calm us down, appease us, infuriate us.

\par A common type of provocation consists of stating or asking something that is obviously absurd but which has the power to hit exactly our weak spot, making us mad, at the same time they pretend not to notice what they are doing. Then, they notice our anger and remove themselves from the argument on the grounds that we are being rude, as if our anger was unjustified. It is a very common procedure that devious women use and whose intention is to put us in a bad emotional state, but that only becomes effective because we argue and talk.

\par Since women are emotionally-driven beings, their attacks are targeted at the feelings of men whom they seek to hurt, bend, and dominate. This happens because they do not have another form of defense: attacking feelings is a way to compensate their physical delicacy and little intellectual incisiveness\footnotemark[32]. Their capacity to make arguments in a focused way is lower, so they attack us by emotional means. Since we, male humans, are rickety and weak at emotional intelligence, and thus childish in this regard, women have a field day. They attack us in many unpredictable ways, avoiding a logical rational confrontation as much as possible and trying to evoke specific feelings, because this is the field that they master and feel comfortable in. Most men fall into their trap and desperately struggle in trying to force them to discuss, while drowning deeper and deeper until he loses the war. And he loses it simply due to a strategical mistake, which I will explain below.

\footnotetext[32]{I know that female intellect is very broad, but it's not very incisive. It's easier for a woman to think of many things simultaneously than to think of only one thing in-depth. This gives them an advantage in certain aspects of life and a disadvantage in other ones.}

\par A way to deal with such a concealed provocation is, first of all, to be distant and untouchable, never letting ourselves get too close.

\par For fulfilling our man's duties in what benefits them, we are always welcome, but for receiving from them the rights that would benefit us, we are always regarded as exaggerated, old-fashioned, sexist, etc., and receive provocations, complaints, deceits, and lies in return. Therefore, the solution is to discipline ourselves internally in order to reach total silence.

\par Silence is a shield; and if any witch provokes you and drives you mad, this is simply because of a previous breach that you left through speech. Do not let yourself be known, because he who lets himself be known is predictable.

\par Once we have shown and revealed who we are, we give them material to abuse our tolerance within our boundaries. Our boundaries are very well measured by what we reveal when we speak, talk, behave, etc. They detect it and seldom cross it.

\par Whenever a man gives importance to what a devious woman says, he is usually dragged into many internal negative states and undesirable behaviors. This influence is hypnotic and occurs through fascination and identification. The ideal state is the one in which we are indifferent by isolating ourselves from the violent magnetic power of their speech and voice (remember siren songs\footnotemark[33]). Although they are physically delicate, many women have a very strong hypnotic power that operates in many directions, through their voice and glance, leading us sometimes to joy, sometimes to wrath, sometimes to despair. Hence the importance of not taking what they say seriously and ignoring their words when they are deceiving. The mere act of paying attention to a deceiving attempt may be enough to trigger an hypnotic crisis, and it is not advisable to underestimate this power.

\footnotetext[33]{The power that female voice has to enchant men is very well depicted in stories of sirens who would drown sailors into the depth of the sea.}

\par Thus, a second care to be taken is to not let yourself be fascinated by the evoking of good or bad feelings. That means: do not get angry, do not hate, do not be happy, etc. Resist to their attempts of eliciting your sympathy as well as your antipathy. Do not be seduced by their compliments, adoringly glances, cleavage exhibition, love letters, gifts, etc. Likewise, resist to the effect of their smirks, hurting comments, attempts to diminish you, belittle you, make you jealous\footnotemark[34], etc. Do not vacillate; hold on to yourself. Be calm. She will unceasingly and alternately try to elicit good and bad feelings on you. Good feelings aim at disarming you, lowering your guard, while bad feelings aim at making you suffer and retaliating you for your stubbornness.

\footnotetext[34]{By resisting bad provocations, we become non-violent. By resisting good provocations, we are not deceived. The ideal thing is always temperance: avoiding extremes. We don't let ourselves fall to one side or the other.}

\par Third, trump her in the art of eliciting various feelings. It is no much use being emotionally bulletproof if, on top of that, you do not correctly attack her by the same means. Observe her and learn to strike her feelings like they do to us. Instead of pointlessly trying to force her into argumentation, simply unmask every emotional provocation and give it right back to her.

\par In short, the solution to deal with annoying provocations is to be more resistant to the provocations than women and, at the same time, be more provoking\footnotemark[35] ourselves, defeating them in their own field. He who trumps women do not let himself get annoyed anymore, but conversely, is refractory to the various provocations. He does not let himself be manipulated because he resists both good and bad temptations, the fascination of affection, of flattery, of challenge, of insult, of sentimentality, of attachment, of arrogance, of indifference, etc. Calmness is the way, the non-action.

\footnotetext[35]{As a natural effect of the mirroring conduct.}

\par As a complement, it is also worth \enquote{punishing} annoying or dishonest attitudes with other in the same vein, within a rigorous criterion of justice, of course, so that devious women can feel how good it is to suffer emotional abuse. If, instead of taking revenge, you turn each annoying behavior into a rule for the relationship, you will tie up a devious woman, who will leave you alone for a while, since in order to hit your feelings, she will have to strike her own feelings first, and will thus stay quiet. For example, if your girlfriend sets up a date and do not show up without giving a reason, do not show up in the next dates and do not hide what you are doing. Inform her that, since she had not shown up to the meeting, you also have no obligation to show up and that the next time she fails to comply with a commitment, there will be an even worse \enquote{punishment} (\enquote{if you did not want to be there, why did you set this up?}). If you catch her in a lie, tell her to never tell a truth again from there on. Obviously, you can revert this decision if there is a sincere regret, shown in actions. If the regret is not fake, it is only fair to give her another chance. We have to forgive if we want to be forgiven.

\par One of the hardest difficulties in dealing with human beings consists in the fact that, typically, if we freely allow and forgive dishonest actions and mistakes, we will be seen as suckers rather than kind. One who freely forgives a mistake is considered an accomplice. Thus, there is no other solution than \enquote{punishing.} The \enquote{punishment} that I refer here is completely different from pure vengeance, because it preserves justice, honesty, sobriety, and reason, preventing worse things from happening. And it is not something that will harm the other person; it will only give their actions back to them, so that they can reflect about it.