\section{The Female Vices and Weaknesses}

\par It is often spoken grudgingly about female evilness. The common trend is to avoid and evade it. On the other hand, denouncing the many undeniable male cruelties is commonplace, which people see as only natural, as it is common to hear, \enquote{all men are no good.} Good men, then, put on a toothy smile and pretend to find it amusing, even though deep down inside, they know that things are not so simple. Hence the need for us to walk the opposite path and clarify what is missing, facing the problem that everyone is avoiding head-on and denouncing it like righteous feminists\footnotemark[36] do with respect to male vices. If it is true that male humanoid animals\footnotemark[37] are mean toward females, ogling them, valuing them for their outer beauty, and always having sexual ulterior motives, it is not less true that females are also mean, valuing us for our social status, our attractiveness before prettier women, our money, our fame, etc., while not loving us disinterestedly. They are totally utilitarian and do not love us for what we are but only for the practical and emotional benefits that we can provide. Male ulterior motives are sexual: the male wants to copulate. Female ulterior motives are practical and conniving: to be envied by her rivals, to be turned into a princess, to have a slave, to draw attention, to be protected, to become known, etc. Thus, not only men are the bad guys in the story.

\footnotetext[36]{Just so we're clear, I refer to self-aware enlightened feminists, not misandric Nazi feminists who blame men alone on the responsibility to the world's misery.}

\footnotetext[36]{We are all male humanoid animals. However, not everyone accepts to be one and there are men who strive to transcend themselves. We are not only humans, as we like to think; we are also animals and there's nothing wrong with that, it's just the current stage of our evolution. Our animality, on its turn, is not always in harmony with instincts and nature. It seems to me unnecessary to mention proofs confirming this idea.}

\par Vices are emotional weaknesses. Emotional weaknesses are the most intense desires of the soul, against which the person has not much resistance. They are secret springs that lead to action. Such springs are triggered when the correct psychological buttons are pressed. The correct psychological buttons are pressed through attitudes that excite and ignite passions, desires, fears, and intense emotions. Hence the importance for human beings to become self-aware of their weaknesses and to overcome them.

\par Despite the virtuosity and nobility of character that are at times apparent, the devious women whom we are dealing with here have desires which they are unable to resist. These desires are tools by means of which such women can be taken, tied up, and manipulated. I will point them out:

\begin{itemize}
	\item to be protected against her natural fears (fear of the darkness, of loneliness, of abandonment, of death, of sickness, of cold, of rain, of getting old, of certain small disgusting animals, etc.), this is her main weakness;
	\item a sweet tooth for sweet, ice cream, and chocolate;
	\item to be recognized socially, to be admired and envied by everyone;
	\item to get ahead of her rivals, to get noticed by a famous man who is desired by many women;
	\item to figure out secrets that excite her curiosity;
	\item to be desired and to reject who desires her;
	\item to dissimulate, to lie, and to feel that she can deceive possessive men;
	\item to continuously prove that she can make a man fall in love with her and that he is lovesick.
\end{itemize}

\par The aforementioned desires are never totally satisfied while she is in a relationship with an experienced man: he boycotts it. Women hold on to those men without understanding why. And the reason is summarized as follows: those men invite women with the possibility of satisfying such absurd passions and at the same time never totally satisfy them, preserving the female thirst.

\par The desire to offer sex, affection, and love \textbf{IS NOT} one of the main female weaknesses. These three elements are just tools used to attract men and dominate them in a manner similar to the one described above. In the war of passion, the desire of the other, whether they are a man or a woman, is never totally satisfied. The one who completely satisfies the desire of the other loses the war. The one who never satisfies any desire of the other also loses it. The one who partially meets all desires of their partner in the most skillful manner, while always allowing those desires to last, wins. That is why the war of passion is foolish and has nothing to do with true love. The war of passion is pure sentimental selfishness.

\par Every desire is a weakness by which a person can be taken. Devious women do not want to love a man unconditionally, disinterestedly, and altruistically, nor do they want sex in and of itself, as unaware men usually think. Their desires are as petty and selfish as the desires of men, only being distinguished from the latter qualitatively. The kind of desires are different, but the selfishness contained therein is not. That is why what they commonly call love is of no use whatsoever. It is something disposable and has nothing to do with true and divine LOVE.

\par Unless a woman has a history of dedication to a victorious struggle against herself and seeks to overcome herself day after day, becoming aware of her debilities, she will cheat on her husband without much difficulty if she is put alone with another man who corresponds to the ideal masculine model that exists in her soul. This is the proof that passionate romantic love is a ploy to deceive innocent people. Passion has a fatal side which nobody likes to talk about. The irresistible ideal masculine model is the one that synthesizes all desires, dreams, fantasies, vices, fears, and longings that confine her urges. Not necessarily the men whom such a model is projected onto will deserve it. Not always will fascinating men attract women toward salvation.

\par If you are being ignored by a lady, such a fact indicates, certainly and undoubtedly, that you are not pressing the correct psychological buttons out of ignorance or inability. But it is very likely that a more experienced man is doing it. Most of the time, unaware men press the wrong buttons, that is, they act in the wrong way, believing that it will have an effect, and having another. Then, they get surprised and confused, without understanding the reason for her rejection or disinterest. And the reason is simply ignorance: the attitudes that he believes would impress women do not impress them, and the attitudes that apparently would scare them away do not scare them away. The effects are always opposite to what is expected, and the would-be seducer can fall into ridiculous situations without even realizing his ridiculousness. Then, we watch tragicomedies which we simultaneously laugh and cry at. Ridiculous attitudes that unaware men believe to have a seductive effect but that actually have the opposite effect are: shouting, trying to be funny, speaking loudly, using pick-up lines, being extroverted, being a bully, being a showoff, making a monkey out of himself, playing the good guy, trying to please her, pretending to be Prince Charming, showing that he is in love, harassing her, chasing her, watching her, showing that he is hungry and desperate for sex or dates. Conversely, attitudes that have a positive effect are: taking no notice of her looks, looking deep into her eyes until she looks away, surprising her by suddenly engaging with her but as if he does not care about such a fact, being serious, speaking in a firm tone of voice, being short and sweet, speaking little, surprising her with long wise speeches, ignoring her presence by surprising her with a sudden approach, disagreeing with her, contradicting her opinions, leading her beneficially, harshly exhorting her, \enquote{horrifying} her in a calculated manner, \enquote{cornering} her, backing elusive devious women into a corner, creating decisive situations, being aloof, closed, and mysterious, speaking little and correctly, being protective, physically touching her in a quick and slight manner as if he had no intention to do it, surprising her by saying sound things and soon getting back into silence, not talking nonsense, not being long-winded, and especially, being just, sincere, and correct.

\par Before a man who leads, stands out from other men, and impresses her with his uncommon firmness and security, females faint and cannot resist it. It is a weakness analogous to that which we feel before pretty, delicate, and voluptuous women who expose their legs, their cleavage, and their shapes, inviting us to love making (even though they refuse it immediately after).

\par In a way that is very similar to children, many adult women need to feel the presence of someone more powerful and more wise who leads and protects them (this is why powerful men are the most flirted with). Outside of this position, they feel vulnerable and exposed to the natural dangers of our species. This is the weakness that impel such a woman to hurl herself at famous men, singers, and artists, because those men communicate to her unconscious that they are more powerful than ordinary men (\enquote{If he really stands out, he must be really powerful and have something good!}). In such situations, fantasies from the feminine unconscious are activated, which makes her take action, offer herself, and chase and flirt with men who stand out. But once she has seduced and conquered such a man, she will be suddenly disappointed if he does not match the demands of her unconscious fantasies. She will then lose interest and replace him with another man, or keep him as a mere trophy, emotional slave, or something like that.

\par Their indifference to sex and reluctance in showing acts of love and affection compensate their physical fragility and give them emotional control over the other gender, which are factors that make women emotionally resistant and hard to win in the wars of passion. Female mammals and fowls are, in general, not eager to copulate, as opposed to males that get an intense stress when forced into abstinence, and they may even develop a pathology. The desperate need for the sex-affection-love triad felt by human males makes them vulnerable and forces them to flirt, please, chase, and subject themselves as servants to a queen. As princesses and felines, human females receive the security and comfort as something that is naturally owed them and whose corresponding price does not need to be paid, because their mere existence is seen as a more than fair payment already. We, males, on the other hand, generally resemble slaves and dogs, because we see it as only natural to sacrifice ourselves, giving them a lot or everything while receiving little in return. Therefore, women are strong in a field where we are weak. To make matters worse, as they know that they are delicious and necessary for our emotional health, they take advantage of our weakness to exercise their dominance. As a rule, a man is a puppet who manages and commands everything, except the female felines who command him. Male superiority is a myth.

\par Some unaware men project their psychological characteristics onto women and believe that women are like them: eager for sex, love, and affection. They believe that the love-sex-affection that they offer would impress women, and that women, in turn, would fall in love with their \textit{phallus erectus}. This is an absurd idea that is not supported by observation and experience, because women work inversely to men, they are our opposite pole.

\par Knowing our weaknesses as they do, it becomes easy, for instance, to tame by means of affection a husband who is enraged by jealousy, or to make a man harass her by exposing herself in order to accuse the harasser afterwards, etc., because all comes from a man's weaknesses (and men themselves are, therefore, also guilty for that). Therefore, we must fight our own weaknesses instead of turning ourselves against our delicious female felines. When we subject our animal side, our needs, our desires, our madness for sex, etc., we unintentionally subject women by extension, even if we do not want to, because we eliminate the buttons and weak spots by which we were being manipulated. In other words, we subject them when we subject ourselves by giving up on submitting them to our interests and emotional weaknesses, namely our desire, affection, and lust\footnotemark[38].

\footnotetext[38]{Of course, when women also become aware of their weaknesses, relationships become more harmonious. The animal stage starts to be transcended and contradictions move on to other levels.}

\par The behavior of devious women is often governed by a principle that I call \enquote{sentimental selfishness.} For them, it is not our feelings that matter but rather their own, and only their own. They are totally blind to anything else. They deem \enquote{logical} what brings them desirable feelings and \enquote{illogical} what brings them undesirable feelings. Here arises another complication and things get messed up: the pleasant feelings are not always the desirable ones, for the unconscious reacts in a way that is different and even contrary to conscience.

\par Sentimental selfishness possesses them and leads them to constantly fulfill their needs of confirming that we are lovesick. When they are unable to detect signs of emotional suffering in their partners, they get sad and tell themselves, \enquote{He does not suffer for me anymore, I must be getting uninteresting and unattractive to him, etc.} They rejoice in seeing us suffer from anger, annoyance, jealousy, longing, sadness, absence, attachment, confusion, doubt, etc. This same need is what strikes them back when they come across a refractory man, as he does not give them satisfaction. Since their desire of confirming our emotional suffering is very strong, such a desire turns into an internal parasite that swallows them alive when it is not satisfied, for the pain of dissatisfaction is proportional to the intensity of the desire\footnotemark[39].

\footnotetext[39]{This is why women should recognize and transcend their own weaknesses instead of heaping vituperation upon who describes them.}

\par As such, the refractory partner will strike a devious woman in her feelings a first time by refusing to be lovesick, and a second time by \enquote{punishing} her with her own actions and unsatisfied desires. If she still does not change, he will have no choice but to leave her.

\par There are extreme cases of violent, predatory, highly hysterical and aggressive females who challenge us to physically assault them (\enquote{Beat me if you're man enough!}). In such cases, there is no alternative for us but to walk away forever.

\par Very few men can deal with this female vice of provocation. Most despair and succumb, as the learning curve is steep, long, and painful. Weak men will shout, assault, insult, and lose the war.

\par Men may be physically and intellectually strong but are emotionally weak. They easily lose their temper when provoked. They are impatient and short-tempered. This emotional weakness makes them be defeated in the wars of passion. The greater emotional intelligence of women affronts and dismantles a man's physical and intellectual strengths and defeats him, tearing him apart and breaking him down. This is why men who resist their influences and provocations at an emotional level become invulnerable.

\par The mind of devious women has difficulty discerning goodness from weakness, as well as cruelty from strength. This confusion makes them feel unsafe in the company of democratic and good men. Thus, their preference for the worst men is based on a misconception. And this misconception stems from one more vice: shallowness of judgment.