\section{The Ideal Masculine Profile}

\par If your relationship is worn-out, your partner ignores you, refuses sex, does not want to see you, etc., this means that the person who you are, as you have always been, is not interesting anymore. Thus, it is time to \enquote{die} and become someone else. Get this straight: \enquote{dying} here means to become another person who is completely different from what you have always been, changing yourself to the point of causing estrangement, a feeling of loss. It is a symbolical \enquote{death}: the real death of your ego, that is, of the psychological person who you are.

\par If you are panicking, desperate, or depressed because your beloved betrayed you or despises you, and you are thinking of committing suicide, I suggest you not to do that. Prefer \enquote{dying} psychologically rather than trying to take your own life or your own physical body. It is better to transform yourself psychologically than to commit suicide, do you not think?

\par If you truly \enquote{die} to yourself, you will in fact become, and not by mere assumption or simulation, someone else. You will not be simply simulating a behavior, but will rather have truly changed. You will not be recognized anymore, and the person who made you suffer will note your odd behavior and will get desperate for losing you.

\par If you are being neglected, this means that you may be making the following mistakes:
\begin{itemize}
	\item Being excessively affectionate;
	\item Talking too much;
	\item Trying to please her all the time;
	\item Showing fear of losing her;
	\item Demanding her attention, affection, and sex;
	\item Demanding her presence and company;
	\item Chasing her all the time, constantly calling her, etc.
\end{itemize}

\par Despite the lies that devious women tell you, the fact is that a very affectionate man gets tiresome and only serves to be rejected and treated like a slave or a stray dog. Affection must be well dosed, rationed. Be affectionate only every once in a while and at the right time: as a reward for her good behavior. Be colder than affectionate but not completely cold.

\par In general, men try hard and greatly sacrifice themselves by flattering and pleasing a woman, only to receive in return a minimal amount of her affection and sex. This is a general trend and you can confirm it by observation. Women are so used to it that every time you sell yourself as affectionate, you will be seen as a chaser who is looking for the sex-affection-love triad. Since women do not like sex too much, it follows that affectionate men are regarded as uninteresting and are utilized as mere emotional slaves who give their all and receive little or nothing in return. The curious thing is that insensitive men, who are very few, are precisely the ones who receive for free and without effort everything that affectionate and chasing men try so hard to achieve. This is because such women do not understand the logic of love in depth. In the field of romantic relationships, the mind of a devious woman works like the mind of a swindler: it is unable to understand the events from a viewpoint that is not their own. The only reference of love that exists in them are themselves, because they live immersed in a natural selfishness. It is thus a waste of time to pressure and demand affection, love, and sex from women who refuse it, because such an act will always have a diametrically opposite effect.

\par Do not be a chatterbox and do not talk much. If you notice, you can see that conversations of such women are usually shallow and subjective. If you get into this frivolous subjectivity by participating of useless conversations and hearing their tiresome monologues, their psychological songs, gossip, the outcome of soap operas, slander about other people's lives, etc., their unconscious will react by regarding you as unmanly, since among the ideal masculine traits are rational objectivity, firmness, depth, superiority, and dominance (this is why they chase leaders). The disastrous effect will be this: your partner will consider you \enquote{cool,} \enquote{gentle,} and \enquote{nice,} but very unattractive as a male. Likewise, you will fall into a ridiculous situation if you keep trying to be funny, to make her laugh, to clown around, to hang yourself upside down from branches, etc., because you will be treated as a cheerful and well-intended clown. Also, do not get into arguments, you must resist the fatal magnetism of a venomous tongue and ignore her useless complaints. Do not shout, because you will be seen as unmanly. We want them to see us as males and not as friends, pets, or clowns, right? Therefore, the ideal thing is to be silent, serious, rough, and talk little. However, our few speeches must be spot on, always in a commanding tone and in a protective and orientating manner, directed for the good and never for the bad. Never legitimize the accusation that men are oppressive and enemy of women.

\par Do not run after her fantasies, trying to fulfill them, because you will be considered a mere submissive slave. We can do that occasionally, but not always because it conveys submission.

\par This is the most difficult part: do not be afraid of losing her. If you have this fear, it will become apparent through your attitudes or during the relentless tests intended to find out who we are. Always be prepared to truly lose her, forever. If you are afraid of losing her, you will show that you do not have other, better, more loyal, more dedicated, more sincere, and prettier women, and that, therefore, you are a second-rate man, unable to get females. You will also convey that you want to pressure her by overwhelming her with your feelings and attachment. Women greatly value detachment and indifference when combined with a protective-leading posture that is beneficial to them. Detachment, sentimental coldness, and insensitivity are considered ideal masculine traits. It must be understood that such attributes are not inherently bad, since they may well be used to fight the wrong things, to protect, and to avoid danger. Coldness is bad when it is geared toward selfishness, but not when it translates as calmness directed in an altruistic manner. This is why women value attributes like that.

\par Chasing them is also a serious mistake. A chaser is always rejected because he conveys that he is unable to get something more important in his life. Chasing conveys weakness, submission, desperation, urgency, etc. Therefore, do not keep calling her endlessly, chasing her all the time, etc. Let her do this to you, and if she does not... too bad! Do not seek her, let her seek you as often as she wants. This way, you will know who she really is and what she truly feels.

\par If she does not want to see you, do not fight it, and if she suddenly disappears, simply forget her, ignore her, and focus on other things, disappearing for even longer, usually for twice as long.

\par Women are used to being flattered all the time in exchange for sex, affection, and love. They have gotten so much used to flattery, gifts, compliments, special treatment, privileges, etc. that they get shocked when a man ignores her. They feel diminished and belittled, believe that they are losing the competition to their rivals, and their self-esteem drops terribly. As a result, they often chase you to seek revenge, in an attempt to reject you once they have bent you over.

\par Do not fall into the trap of the good, democratic, and malleable boyfriend. Be democratic if she deserves it, but be firm in your viewpoints and only change them if mistakes are demonstrated objectively. If she fights it, wreck her arguments and crush them (note well: her arguments, is that clear?) mercilessly and without hesitation. The act of giving in is signaled as a weakness of mind for indicating too little firmness of purpose and weak willpower. Malleability is never recognized and reciprocated but, conversely, it is taken advantage of as an opportunity to abuse the other. A malleable man is seen as a sucker and not as a wonderful man. Women seek men who lead, dominate, and protect them, not servants who satisfy their capricious desires.

\par The ideal man, modeled according to our goals, talks little and accurately (this is just a model for reference). He uses a serious and imperative tone of voice. He speaks in a tone of command. He does not ask his partner for her permission: he orders, but does not force her to obey, giving her the right to refuse. He does not talk about himself. He does not complain. He does not confess his weaknesses. He does not cry in his partner's presence. He is not a chatterbox. He looks into her eyes suddenly, in a fixed and firm manner. He does not observe her all the time, only every now and then. He does not watch over her: he almost ignores her existence. He does not argue. He does not polemicize: he simply informs. He is a king in his own kingdom and not a servant. He does not miss her. He does not chase her. He does not look at other women's body, because he is neither lustful nor a fornicator. However, when his female finally seeks him out for sex, he shows his strength in an overwhelming wild sex like a hurricane. He is an earthquake in bed. He does not use pick-up lines: he pleases effortlessly. He does not shout. He does not let dirty tricks pass unchallenged: he knows how to return them. He is not a clown. He is not funny. He does not laugh too often: he only smiles slightly once in a while. When he finally laughs, there seems to be something strange about his laughter. He takes the deal in situations. He dominates the relationship for good and not for evil, treating the woman like a girl. He does not bother his partner by asking her opinion all the time. He does not get annoyed at provocations: he knows how to return the consequences to whom has provoked him. He is impenetrable, distant, and mysterious. He neither forbids nor takes revenge: he returns the consequences, rewarding sincere women and making insincere women who attempt to deceive him answer for their actions. He does not run after lies, because he does not care if he is being deceived or not. He does not commit for free: he charges a high price. He is a prize. He values himself. He is not affectedly sensitive. He is not delicate. He may have plenty of money but disregards it. He is above social prejudice. He is not a moralist, a \enquote{straitlaced} guy, or a friend of good morals. When he enters a room, he draws women's attention because he ignores them. He does not beg to be loved. He does not need passionate affection to be happy: he despises it for knowing it is false and hypocritical; he prefers true love. He helps. He orientates. He looks after. He protects. He guides. He does not do injustice to his partner. He always keeps truth on his side. He is disconcerting. He surprises. He is not predictable. He is not moved by crocodile tears; he is only moved by real tears, which he knows very well how to identify. He does not run after capricious complaints. He fuses opposite traits together. He is simultaneously good and, in a way, \enquote{bad,} indifferent, and protective. He punishes adultery with a permanent final breakup, or with despise. He never commits a passionate crime. If he is betrayed or deceived, his mere absence and despise are enough to punish the betrayer, who will suffer for being unable to find someone like him to replace him. He is the best, because he does what no one else does: he treats her like a girl, making her feel like a child and reminding her of her childhood, rather than deifying her and putting her offerings at the altar. His heart is gold, and he charges a high price to commit: total, plain, and transparent loyalty. He is an incomprehensible mystery. In short: he is a real Man.

\par Of course, no mortal man would mathematically, fully fit this model. But the model serves as a reference for us to get close.

\par When a man is not being noticed by a woman, he usually clowns around, chases her, makes use of pick-up lines and flattery, eagerly ogles her, etc. This indicates that he is unaware of this science and is not behaving as he should. If he changed the way he treats her, replacing his chasing behavior with correct attitudes, her attraction for him would be triggered. The need to chase shows ignorance of the behaviors that generate attraction. A man who behaves properly does not need to chase. The only women who accept hungry, desperate, and eager chasers who make use of dull pick-up lines and have hungry looks are the desperate: women who have starving kids and urgently need a provider, spinsters who have not lost hope yet, women who are a pain in the neck, etc. If, against all odds, an interesting woman accepts such a repulsive behavior, she will accept it for some other reason, such as money or status, but never because she was attracted to him.

\par The fact that we are not chasers does not mean we must stay passive, waiting around for a woman to fall from the sky. You can and even should take the initiative by acting as a male who makes an impression, psychically strikes her, amazes her, and even positively shocks her (positively, just so we are clear!), but never as a weak desperate chaser.

\par The act of positively \enquote{horrifying,} as explained in the first volume, consists of breaking enshrined ideas by behaving in a manner totally opposite to the common one but which is well-calculated, that is, it is a behavior that sets a man apart from weak men. This requires a lot of skill, since a slight mistake can have the opposite of the desired effect. \enquote{Horrification} must be positive and not negative (keep this well!). Here is an example of positive \enquote{horrification}: giving an order, in a serious tone, that counters what a beautiful devious woman is doing but which ultimately benefits her and protects her. This attitude runs counter the tendency of all weak men, who hasten to please her and submit themselves to her, instead of treating her \enquote{with the sword}\footnotemark[40] as Ulysses did to Circe. Men who are unable to counter her are enslaved by animal passion and are turned into pigs like Ulysses' men. A superior male not only commands her, but also contradicts her and does not really care if she likes it or not. He does not worry about reproaches, disappointment, etc., since he does not want to impress her, but precisely by renouncing the act of impressing, he makes an impression.

\footnotetext[40]{The sword is a symbol of phallus.}

\par When talking about the ideal masculine profile, the one we are trying to model, a dangerous mistake usually occurs. I will expose it: there are two ideal masculine profiles. One of those profiles is ideal for meeting selfish feminine goals, whereas the other is ideal for meeting masculine goals. Usually, the ideal masculine profile, described and shown in movies, magazines, soap operas, interviews, etc. is fake, because it only corresponds to selfish feminine goals: this would be a sweet, sensitive man who sends flowers, is hard-working, honest, affectionate, and who has money, always at the disposal. Since this goal is totally conniving and selfish in the ends and in the means, it has the opposite effect to our goals and becomes disastrous to our lives when we adopt it. Almost all women are unanimous in stating that such a man is ideal and that they would love to have him by their side, but they do not say for what he is ideal nor for what do they want him. I tell you: he is ideal to be an emotional slave who gives them love while he gets coldness, cheated on, disdain, abuse, etc. in return.

\par The ideal masculine profile that I have described and tried to model here is not at all that soap opera profile that women describe. It is an ideal profile to protect yourself against love domination, manipulation, deceit, lies, dissimulation, disrespect, and cuckery. It may sound contradictory, but this is a profile that also benefits women, even though they protest against it when they are being inconsequential.

\par It is indispensable to resist a woman's fascinating influences in all its forms. Fascination is hypnotic, and we can define it as an identification of ourselves with external facts. Contrary to common sense, fascination operates not only when there is sympathy and charm, but also in negative situations of conflict. Hostile words, offense, insult, provocation, mockery, etc. cause as much fascination as compliments, affection, promises, etc. Fascination for negative attitudes causes negative emotional states. Whether you are mad with rage because you have been double-crossed, happy as a clam because you got what you wanted, or sad because you have been abandoned, etc., you will be fascinated by those events. Thus, we must be fascinated neither by good nor by evil.

\par You will not be able to simulate the ideal masculine profile that I modeled here. If you only try to pretend to be this way without really being so, things will backfire: you will develop emotional diseases and will be unmasked in the selective tests for reproduction driven by a woman's animal instinct (we all have animal instincts, no one should take offense to this), and will fall into ridiculous situations. Female instinct has an ancestral wisdom developed since prehistoric times that allows females to quickly identify a phony male who wants to mate. Be a real Man with a capital M. But for this, you must die to yourself and become someone else. It is a hard, tough task. Many fail in this attempt.

\par Men of today seem ashamed of being who they are. The trend is about being affectedly sensitive, and anyone who waves the flag of masculinity and heterosexuality is deemed prehistorical, troglodyte, retrograde, and sexist. The male is cornered. It is often said that we are good for nothing. However, all women remember us in times of danger and hard tasks. No one dares to call us good for nothing when floods, earthquakes, and fires occur. And if it were not for us, men, our species would not have survived the natural dangers and beasts since prehistory. Who would hunt mammoths and fight saber-toothed tigers so that women would have protein to eat? Who would enter rivers crawling with crocodiles, piranhas, and serpents to bring them fish? Therefore, it is not mandatory for one to have a uterus and bear life in their womb to be indispensable. Of course, without women we do not exist and their importance were never denied by real men. No man would imagine a world without women. Likewise, the intrinsic masculine characteristics that I described above are and have always been indispensable to women, in spite of what they say. Those were the characteristics that allowed men to wage war and hunt beasts to defend them.