\section{A Violent War of Nerves}

\par You are either alone or with someone whose company is pleasant but does not fulfill you as much as you need. Meanwhile, your beloved is having a great time hanging out with other people.

\par You miss her but she does not miss you. You are always the one to take the initiative to seek her, but the opposite never happens. You always take the initiative for the calls: you have to give her many calls before she answers it. You extend the conversation on the phone until she makes poor excuses for ending it. She is always the one to hang up first.

\par You are always curious about what she has to tell you. She is never interested in what you have to say.

\par You give her countless certainties that you are loyal and love her, but you only receive doubt, inconsistent facts, and fishy stories in return.

\par She makes a promise to meet you, and you keep looking forward to the meeting for a long time, but she thwarts you. Her explanation fails to convince even a mental patient.

\par Desperate, you withdraw, but you are not missed at all. Instead, it seems that your absence pleases her even more. Then, you realize that you need her a lot, but she does not need you in the slightest bit. For you, there is nothing more important on this Earth than her, but for her, there are many other things more interesting than you. You are replaced with her female friends, male \enquote{friends,} relatives, parties, trips, pubs, or even with a mere television show.

\par You are an open book: she always knows where and with whom you are. On the other hand, you never know for certain whom she is with and what she is doing.

\par You feel like you are in hell and she feels like in heaven, which is why she is a goddess, and you, a doomed man. She is your goddess because you have put her on a pedestal.

\par When she finally shows interest, you are there, available, as if you have waited for all eternity for this moment. She momentarily graces you with a little of her wonderful presence, but she soon withdraws, so that you once again wake up from your dream into a nightmare.

\par Welcome to Hell! The merciless war of passion is underway and you are being defeated day by day. You may die of sadness, by somatizing diseases, or go mad. You may commit a crime. Your mental torture makes her immensely happy, because she is nourished by your disgrace. She feels like she is the best, the hottest, the prettiest (even if she is not), a super-female for having the power to reject you and trample you down.

\par You try to defend yourself, but you realize that you are unable to, that you do not have the strength. The only strength left that you have is your muscular brute physical strength and your logic, both of which are useless in this war. Muscles are not useful, and logic is even less useful.

\par The more you argue, the worse things get and the more your problems entangle and aggravate. You try to make her understand your obvious viewpoint, but she plays misunderstood and turns the conversation into chaos. You complain, but all you get as an answer is, \enquote{You're insecure,} \enquote{You don't trust me,} etc. It is no use appealing to her logic, because everything is crazy, insane, illogical, absurd, calculatingly stupid, and irrational.

\par If you lose your head and assault her after so many provocations, you will have fallen into a trap: you will prove to be a cowardly villain who assaults a \enquote{fragile being who only knows how to give love.} You have been tied up and dominated.

\par You know that disappearing is not the solution because she will not come after you and you will lose her forever. She knows that even after many years without seeing you, you will be there, available. You mean nothing to her because you do not have anything interesting, and thus you will not be missed. But you do not want to lose her. It turns out that you do not have anything that she actually wants or needs, whereas she has many attributes without which you would not survive: her specific way of being, the way she looks at you, the way she walks, her voice, her touch, etc.

\par You have been had, fallen into an emotional trap. It was all a lie: the love in her eyes, her smile without guile, her delicacy, her purity of feelings, her fragility, her defenseless look, her affection, her words of love. She tricked you, played with your happiness, your sincerity, and your most noble feelings. Your mistake was falling in love, regarding her as unique and special.

\par Now, the only solution for you is to give up on everything and put an end to it. So, put an end to yourself and \enquote{die} psychologically, eliminating from within yourself this venomous feeling that has thrown you into such a miserable state. Do this and you will see how things will slowly change. You will realize that your goddess was made of clay and her divinity was a fraud. You will throw away the disenchanted statue of her.

\par I tell you that you were deceived all this time. You were hoodwinked by passion and now see the world upside down, inside out. There are many important and interesting virtues inside you, but you are unaware of them, you do not know them. Dig them up. There is another man within you, wake him up. Stop loving passionately. Stop missing her. Stop fawning over her. Stop chasing her. Do not waste your precious time thinking about her; unmask her mercilessly. Treat her for what she really is: a female. Ignore her crocodile tears. Denounce her lies and unmask her pretenses in the moment that they are underway. Ignore her fake cry. Make her see who she really is: an angel-faced devious woman. Do not let her run away from herself. Teach her a lesson in feelings that she will never forget and that will teach her not to play with anyone's happiness ever again.

\par Yes, she needs you, but neither of you knows that. What attributes do you have without which she could not live? Many. What does she madly need? Your orientation, your protection, your leadership, your initiative, your logical rigor, your lack of inhibition, your security, your determination, your certainty, your coldness, your firmness, among others.

\par She wants you to be the greatest, to have the upper hand so as to safely lead her, so she resists. She wants to have reasons to respect you and to feel protected at the same time, so she provokes, attacks, and challenges you. She wants to measure your ability to not be deceived, so she lies, plays dirty, and tries to play tricks on you. She wants to measure your ability to not be persuaded, so she offers false affection. She creates a psychological hell and delights in seeing you dance on the fire. It is the most brutal animal instinct in action: the female instinct of male selection. If you fail, you will be discarded from the generic history of your species, and do not bother explaining her your reasons because that will not sensitize her. She will have no mercy, because you are a man and, therefore, were born to be tough and to suffer, to \enquote{handle anything,} and if you are weak, then you are good for nothing. She, and not you, is sexist.

\par Many women cannot feel attraction and mercy for a same man. But, unfortunately, some can feel attraction and fear simultaneously. Other women can also feel attraction and sadness. These women do not love men who want to make them happy, but rather, they love men who make them cry, which makes them unhappy. It is the way of nature. And unless they strongly fight themselves and their instincts, this is how it will always be, disgracefully.