\section{Getting Them to Reveal Themselves}

\par Let us take up the thorny point related to the hidden, true nature of women. There is much in this nature that is wonderful and sublime, but there is also much perfidy that is expressed in varying degrees, according to a woman's personality. While you can hardly notice this perfidy on some women, it is quite evident on the devious women whom we have been dealing with in this book.

\par The general tendency is that such women are dissimulated, faking shyness, modesty, inexperience, decency, purity, and naivety when it comes to sex. Behind the mask, however, a sensual imprisoned female may hide by fear of male authoritarianism, jealousy, and possessiveness aimed at preserving exclusivity. This hidden sensual female may express herself clandestinely to a greater or lesser degree, according to the courage that the woman has to break the rules imposed on her that create the need for her to maintain the appearance of holiness and chastity. In some cases, this hidden side is so repressed and faded that it may only be detected in dreams. In any case, there will always be repressed personality traits as part of her sensuality.

\par It is extremely hard to get this hidden side to reveal itself if you are a husband or a boyfriend due to her ancestral, and justified, fear of masculine reactions. As the general rule is that men are territorial and possessive, demanding exclusivity\footnotemark[41], women pretend to be like this to please us. The result is that we date, commit, and get married to a mask, to a person who does not exist, and it is our fault.

\footnotetext[41]{Men make a mistake in demanding exclusivity. Exclusivity must not be demanded, it must be given. A man's territorial instincts, which make him possessive, is one reason that force women to dissimulate their behavior. Thus, a man who overcomes them receives exclusivity in sex and exonerates women from the need to dissimulate.}

\par This is why husbands hardly truly know their wives, and obviously suffer from it their whole lives. There always seems to be a mystery, a question mark in their heads, \enquote{How would this woman behave if she was left alone with another man? What are the limits of her loyalty? To what extent am I the exclusive owner of her desires and her sexuality?}

\par Unlike husbands, who are usually rigid and moralistic to their wives, libertines and immoral men know and enjoy precisely the female side that is hidden at home and lives in the limbo, in the darkness, and in the underground. This happens because women believe that their forbidden acts will not be reproved by a libertine, but will rather be approved, encouraged, and conducted by men who are on the opposite side of the marital role. It follows, thus, that only if we are immoral and encourage socially-prohibited female behaviors, we will know who a woman really is.

\par At the first sign of conservatism or prohibition on our part, a woman will retract and begin to simulate a politically-correct, socially-respectable behavior to meet our demands. We see, thus, that the best way to know them is to show that we are precisely the opposite.

\par If you conquer yourself and the ability to total acceptance, revealing yourself as a totally liberal man, the kind who likes his partner to travel by herself, to have \enquote{harmless} male friends, to visit women's clubs, pubs, etc., and if you manage to make her really notice this, you will know who your partner truly is and what can be expected of her. But you have to show it perfectly, or you will be deceived. For that, you must not be in love.

\par As correctly demonstrated by Eliana Calligaris, women have a strong need to live the side of life that they were forbidden. This is one reason why immoral men, libertines, scumbags, swingers, Don Juans, etc. attract them so much. These men are the living possibility of experiencing what their parents and husbands deny them.

\par Your partner will never reveal herself if she realizes that you are moralistic. However, we, men, are territorial by instinct. Obviously, we want our female only for us, and this is a legitimate right. But it is not right to force or forbid anyone to do what they want, because every person must have the right to be in charge of their own life. If even believing that we are completely amoral, our partner still remains firm in her exclusive dedication to us, rejecting \enquote{modern} behaviors, this will indicate that she may possibly have a vocation to be a good wife, because she will have offered us her loyalty without us demanding it, without us pressuring her.

\par Almost every heterosexual man is, deep down, a moralist. Even the most immoral libertines usually prefer as a wife a woman who keeps other men very far away. It turns out that libertines pretend, posing as very understanding and tolerant. In actuality, human males are exclusive by nature. Men tend to be prohibitive, which gives females very fair reasons to deceive them and circumvent their ridiculous prohibitions, while mocking them in their hearts. The solution is not to be prohibitive, but rather to accept everything that is thrown at us so that we can find out who the person that we have by our side truly is. Once we discover the truth, we can make a decision that seems the most correct to us.

\par When devious women lie, they do it by defending the opposite of what we know. For instance, if a husband searches for his wife at a place A where she was supposed to be, as per usual, and later lets her know it, she will possibly defend herself with the following lie: \enquote{No, today my routine changed and I went to place B instead.} As such, in order to induce her to tell a wide-open lie that she cannot dissimulate, deny, or escape from, it is enough that the husband, instead of telling her the truth that he was at place A (a true fact), keeps such information to himself and firmly conveys in the conversation the idea that he did not find her at place B or in other places (false facts), even if he has not been there. Then, to deceive him and get away with it, the dissimulating woman will attempt to lie by saying that she was at place A (the place where she believes that the man has not been) and will be caught up red-handed. In other words, we must deliberately make a devious woman lie about something whose truth we already know in advance so as to catch her in the act. This will only be possible if we do not let her know what we actually know and what we actually ignore. The devious wife in question has to believe that her husband verified her presence at place B and not at place A. Once she believes that he did not verify her presence at place B, this will be precisely the place used in her lie. This is just one example among many.

\par The difficulty in catching a lie lies in women's natural specialization in the art of lying, deceiving, and dissimulating. Thus, we must outperform them even in this art\footnotemark[42] if we want to know them. The female intelligence in the field of concealment is enormous and allows them to move with ease between false facts and true facts, with only very few men being able to outperform and corner them. The best way to catch a lie is by eliciting a devious woman into lying more. By the very logic of the deceiving act, the distortion must occur on points that she believes that we are unaware of. In other words, we must trump a lying woman in the act of deceiving by tricking her into believing that she is tricking us. It is only when we accept lies and have a nerve more than the person who tries to deceive us that we can find out the truth behind their intentions. Unfortunately, as Schopenhauer said, lying has become a law in this world. So, to uncover a lie, you only need to accept it instead of getting angry at it.

\footnotetext[42]{Without applying it unjustly or for selfish purposes.}

\par The act of lying and deceiving is a psychological game. The most skilled one wins. The ability consists of conducting the beliefs of the other. In the case of devious women, the one who finds out the truth encourages, stimulates, and elicits the other party into lying precisely about what is already known, leading the deceiving act to a point where false statements become ridiculous by their obviousness. Obviously, if the person is being sincere from start to finish, which hardly happens, you must reciprocate such nobility of character on par.

\par This tactic to dismantle lies by accepting them serves for both genders and may also be used by wives who want to unmask their lying husbands. I am talking about lying women only as a matter of focus, since the book is about the lovesickness of men.

\par Lying is not something praiseworthy, but I see no better way to peacefully unmask deceptive people than to make them lie more. However, even so, we will still be on truth's side: the truths that we omit in such a counter-manipulative maneuver will be revealed to the deceptive person once they realize that they have been caught up in their lies. To the extent that, ultimately, we do not fall low into the vile abyss of becoming liars while we set out to reveal falsehood.

\par A common characteristic of lies that often allows you to quickly detect it is the tendency to avoid a specific subject and a resistance to talk about it, give explanations, etc. If you mention a specific fact, place, or person and a devious woman quickly try to brush you off or change the subject, this indicates that there is something wrong related to the topic and that something is being kept. An insistence on avoiding a topic is a strong indicator that a lie is underway or about to be told.

\par Female dissimulation is and has always been a major problem to men for not allowing them to know whom they are dealing with, what they can expect, what expectations they can nourish, etc. By the means that I have pointed out here, however, we can outwit it if we stay calm enough. I must say that erratic men end up giving cause to be deceived. Fortunately, devious women are better at mitigating suspicion than at supporting their lies.