\section{The Pursuit of Continuity Makes Them Flirt}

\par It is not until they feel that male interest has almost vanished that certain women flirt with men. Flirting, mainly explicitly sexual flirting, is the last resource that they resort to when they see no alternative. Since women do not like sex much, only as a last resort do they resort to it.

\par What motivates women to flirt is the desire for the continuity of male interest, which is extremely strong and whose satisfaction directly interferes with female self-esteem. The desire for continuity seems to be the strongest female desire and the factor that leads them to offer themselves to men who reject, despise, or simply do not notice them. Any man who, at least once in his life, has had a relationship with a woman who does not arouse the slightest attraction in him knows that. Instead of punishing the man who despises her with the same despise, which would be logical, sensible, and correct, the almost rejected woman insistently keeps chasing him, trying to bend him over and make him reverse the way he treats her, while she desperately tries to be loved. The most interesting thing is that, if she really manages to pull off the reversion, she proceeds to avoid him in a dosed and calculating way, because her goal of becoming an object of interest was met and now, for his interest to be continuous, she needs to excite his desires without satisfying them, while preserving his hope. A devious woman plays with a man's hope, and her goal is not to love him but rather to be loved.

\par A same woman who is chasing a man who rejected her for arousing his aversion, will very likely reject another man who is chasing her for arousing passion, interest, and desire in him. What will define whether she is chasing or fleeing will be the satisfaction or not of the violent female desire to preserve the continuity of male interest. She only wants to hold him captive, desiring her, and nothing more.

\par The desire for continuity is the desire to exercise power over a man's soul through his sexual and emotional needs, which must be ignited to the maximum and never satisfied.

\par This desire for continuity is what a seducer triggers in women to make them chase him. Women seem highly vulnerable to male rejection, just like we are vulnerable to cleavage, miniskirts, and voluptuous female behavior. The main female vulnerability is the desire for the continuity of male interest. Obviously, there are other strong vulnerabilities, such as the desire for protection against what they fear, for having money, for humiliating their rivals, for taking revenge against men who rejected them, but the desire for continuity seems the dominating vulnerability, which the other ones only add up to. Envy of their rivals is what drives them to conquer a man who is accompanied by a beautiful woman. Curiosity drives them to try to attract a mysterious man. The desire for power is what leads them to ingratiate themselves to the richest men. Fear leads them to seek protectors and leaders. But all these cases are left behind by the desire for continuity. The various female vulnerabilities mutually reinforce each other, giving an overview of emotional weaknesses through which women can be taken by ill-intended, worthless men, but also through which they could be raptured by good men, if these pay attention to what we are pointing out here.

\par Usually, a woman unconsciously assumes that there is always some male desire, even if tenuous, directed at her. She believes, without being aware of it, that the stranger who is walking across the street would not refuse a sexual offer if she made it. She believes that she is desired. She believes that if she offered herself sexually, her offer would be promptly accepted by the stranger. Some women even believe that every man is a potential rapist and, therefore, someone who desires them. This unconscious belief gives them emotional stability. It is a belief in the continuity of male interest and a necessity for the female psyche.

\par When her unconscious belief in the continuity is shaken up, an emotional malaise forces her to reestablish herself, driving her toward the man who shook her up.

%TODO chained or enchained
\par Why do women desire the continuity so much? Simply because it gives them present and future guarantees in favor of what they desire and against what they fear or hate. Women see men from a pragmatic and functional viewpoint. Their coldness, with respect to being supportive to a man's emotional suffering, does not imply indifference toward the benefits and guarantees that this very suffering provides them, and to tell the truth, the more we suffer from love, the more guarantees of continuity we give them. Our torment in love and sexual frustration show that we are caged, enchained by passion, and that we have a continuous interest in the woman who chained us.