\section{A Way to Reverse the Continuity}

\par There is a very efficient procedure to make a woman who wants to subject us through passion get attached to us, whether she is a girlfriend or a wife. It consists of us periodically practicing wild, intense sex, without a shadow of passionate sentimentality, aligned with a protective leading posture and more or less prolonged absences, without any shadow of a chasing behavior.

\par With this procedure, we can reverse the continuity of interest, making a woman continuously interested in us (is that not what she wanted for us?) and returning the spell she has cast onto us back at her. However, I do not recommend that you use this on many women simultaneously, let alone on married women. Remember that her husband is a man like you, who suffers from emotional pain, and that the couple may have kids who will have their home broken up. Moreover, polygamy seems to be a prison in which a man becomes a slave to an ever-growing number of women, seeking satisfaction without ever finding it. In this vicious circle, a polygamous man goes on stealing women who should be destined to other men. I also do not recommend that you apply this procedure if a woman is cooperating and being understanding and supportive to your emotional needs. This procedure must only be directed at dismantling a trickster's tricks. Considering that, in the case we are assuming, the intention to enslave us through passion exists since the beginning, it seems fair to me to return the dishonesty, by offering ourselves like slaves in love while strictly refusing to be such, thus thwarting the plans of a devious woman.