\section{The Pretenses of Misunderstanding}

\par A common and very efficient female ruse to escape from our psychological \enquote{cornering} consists of women playing misunderstood before what we tell them, at the same time they try to fuel the discussion by emotive means. As understanding of the other is always necessary for a discussion to proceed, it follows, then, that we get trapped in our foolish attempt to make them understand our viewpoint. It is a foolish attempt by the simple fact that the refusal to show understanding already exists and it is the very core of the manipulation strategy. Arguing or conflicting with women is always a loss: if we win them over, this will be a humiliation for us for being an act of cowardice; if we are defeated, it will be an even greater humiliation. Thus, they are beings whom you can barely talk to in moments of conflict. It is not by accident that men who seek them only for sex and ignore them the rest of the time do well.

\par A possible solution for these cases of pretended misunderstanding consists of us simply ignoring the female viewpoint and presenting our ideas one-sidedly. In other words, we win an argument when we do not argue. At a more refined level, we are able to speak very little most of the time. In any case, whenever there is a need to inform something important and unpleasant, we must do it imperatively, ignoring any attempts of polemicizing.

%TODO "from any unmasking" or "from being unmasked"?
\par A typical pretense of misunderstanding occurs when, playing naive, devious women make believe that they do not notice the explicit intentions of the males who surround them, refusing to acknowledge the implications of their forgiving and tolerating attitude toward them\footnotemark[10]. By simulating naivety, they stay safe from being unmasked.

\footnotetext[10]{It's worth recalling that men are not without sin and always have ulterior motives, which is not a surprise for anyone. Therein lies one reason for the jealousy of husbands and boyfriends when their partners decide to get intimately closer to a \enquote{harmless male friend.}}

\par A pretended misunderstanding protects women against a logical and upfront conflict of ideas, which would force them to acknowledge their mistakes. It prevents us from finding out what the edge of their understanding is, and thus restrains us. Again, we find here reasons to be indifferent toward what they think and not to fall in love. Being dispassionate, we are indifferent. Being indifferent, our patience multiplies to infinite and we have no fear of creating a decisive situation.

\par Difficult situations like these are true emotional puzzles, and, again, can only be solved by means of making enclosing one-sided decisions that lead women to a dead end.