\section{The Main Psychological Hell}

\par We can define this psychological hell as a situation of intense emotional suffering stemming from doubt and confusion with respect to the feelings and loyalty of the person we love. This emotional suffering is a real thing, exists objectively, and can be attested by anyone.

\par What most torments us in love is not the possibility of us being replaced, considered inferior to other men, etc., but rather the hell of doubt resulting from ambiguous behavior. What makes living together unbearable is not the \enquote{immoral} desires of our partner, but rather the lack of honesty. Women's rights to decide what to do with their own lives, their own feelings, and their own bodies is inviolable and must always be respected. What is dishonest is the attempt of exercising these rights without bearing the inevitable consequences.

\par In order to get away with the natural consequences of a free sexuality, devious women have specialized in the art of lying, dissimulating, and deceiving, so that they can enjoy certain benefits without compromising any others. The result of this specialization is that they have become walking lies, people who cannot live without hiding things from their father, their boyfriend, their fiance, or their husband. The only stage of life in which such women are transparent and do not dissimulate is childhood. When adolescence begins, they start their first acts of concealment from their father, often with the complicity of their mother. The first acts of concealment prepare the teenager for later concealing other men who will come into her life. It marks a preparatory stage in which her mother fulfills the role of initiator.

\par It is extremely painful to discover that our loved woman is an insincere devious woman who try to give us the shaft just to feel better, smarter, and hotter than her rivals. The act of feeling pleasure in deceiving, manipulating, and tricking a person who sincerely loves them is extremely horrible because it abuses the most noble of feelings: love.

\par The main female strategy in these wars of passion is behavioral ambiguity. Women say and act in a contradictory manner to confuse us and prevent us from knowing what they really feel for us and what they want (for instance, they say they want marriage and commitment on our part, but at the same time, they say they want freedom, or, conversely, they say they want an open relationship, but demand our love, affection, and feelings). They do it on purpose to baffle us.

\par The solution to win these battles is to create decisive situations that force women to reveal through their actions what they truly want, think, and feel. Do not expect confessions or sincerity in their words.

\par In love, it does not count what is said but rather what is revealed through concrete attitudes and actions. Learn to see what is going on without having to ask, without needing confession. In cases of insurmountable uncertainty, we have to be realistic and choose the most likely conclusion: that human beings are more easily prone to selfishness and to take advantage of the other in order to reap the most benefit. A devious woman will never admit she flirted, was attracted to, or had sex with another man. Thus, toss confession aside and make your decision from the first indications. If she really loves you, she will recover lost ground and try to prove her innocence (!). If she does not make a move, then you will not have lost anything since she was not worth it anyway. A woman who is incapable of love is not worth a dime and these exist galore everywhere. Cheaters do not deserve that we cry for them and are not even a shadow of sincere women, who are valuable and precious.

\par If your partner is irrevocably weird, different, distant, arrogant, or cold, and is treating you badly, consider the relationship lost and benefit from it as much as you can while it lasts. Do not waste your time questioning, trying to understand what is happening. Just enjoy whatever good is left, until it is over. When she does not want to give you anything anymore, simply abandon her without giving any explanation, just like this kind of woman likes to do to us. Above all, do not argue, do not polemicize, do not fight, do not take revenge, do not try to prove yourself right, do not insist on your grounds, and do not explain your reasons, because that will only worsen the situation.

\par Considering that dissimulation is the main tool of devious women, experience has shown us that the master guideline that good, sincere, and honest men should follow for dealing with such women is the capacity to find out what is beneath the confusing behaviors with double meaning. The whole strategy seems to come down to the capacity to create decisive situations that give no room to evasion or dissimulation. Doubt is our worst enemy, and we must create situations to get rid of it, which requires a lot of determination.

\par Hellish games involving doubt are aimed at forcing us to show that we suffer a terrible lovesickness, or a crisis of absence or of jealousy, and are never admitted by those who practice it. Such games move in the shadows and obscurity, while a devious woman acts as if nothing is happening or has the nerve to expressly deny everything when questioned. Confrontation is always avoided for being clarifying. When we try to confront her, the conversation is diverted to a subjective argument, controversy, or capricious stubbornness that preserves doubt, confusion, and uncertainty. Regardless of any consequences, she will never admit what is obvious, which is why it is totally useless to talk or to try an open, explicit, sincere, and honest agreement. It is equally a waste of time to demand clarifications, or transparent, decisive, and consistent behaviors, etc. It is best to just observe them and make a decision on our own.

\par It is very common that, after many days of stable and peaceful treatment, she suddenly suppresses certain demonstrations of affection which her \enquote{victim} was used to. At the same time, she will preserve other loving acts to create an uncertainty that confuses her partner. She always does it when we are not expecting it, in the moments when things are going well, so that she can caught us off-guard. The purpose of this manipulative act is to force a man to show that he is suffering and is still in love. It is a periodical test aimed at measuring the degree of his dependence and evaluating his passionate submission. If you get upset, you will show your suffering through your body language and will make her happy as a clam. The best solution to tear up this hellish game is to simply withdraw into silence or break contact with her immediately after you detect the slightest hint of awkward behavior. Then wait, wait, and wait. If you are approached by her, unmask her and forever rule out of the relationship those same loving gestures which you were denied. If she does not seek you, be glad because this means you had a creature by your side that was good for nothing but lying.

\par Precisely because they take place in obscurity, hellish games of feelings are hard to detect, predict, and counter. The difficulty is aggravated by the fact that our credulity (leap of faith) in words is not recognized as a virtue and reciprocated with sincerity. On the contrary, credulity is seen and exploited as an opportunity for them to deny everything that is happening, and thus to deceive us and to keep us confused.

\par There are cases when a man gets annoyed at his devious partner for her superficiality, her insistence in taking his precious time to offer him \enquote{spiritual} affection with a useless talk about frivolous subjects, instead of practicing hot wild intense sex, etc. Sometimes, it even happens to a man to get impatient at how affectionate this kind of partner watches him. Such an impatience is due to him falling out of love and is felt by her as a rejection. It is curious that, almost always, she insists in offering her love and stays in love with him while she is offered a glimpse of hope to revert the situation. If you think that this insistence in turning rejection around with an offer of affection is a proof of the altruistic superiority of female love, you are mistaken. What really happens is that a manipulative female cannot stand losing the wars of passion, and tries to break a male's resistance so that she can then take revenge, because what she is looking for is to be on top, to lord it over the situation. In order to keep her in check, just reject her and, at the same time, give her an airy hope.

\par Games in the war of passion can be reduced to concealing one's true intentions and, at the same time, finding out the true intentions of the other. The one who is the most mysterious will confuse the other, and by being more realistic and observant, will win.

\par Besides the main psychological hell, there are other psychological hells in love. One of them is the very well-known situation in which the person who is in love is put aside by the loved one, who has fun and a wild time with other people, and totally ignores their suffering. Only a complete revolution against the curse of passion can subvert the positions in this case. The poor victim of the spell feels like their strength eludes them, that they are lacking it, and do not feel the least energy to fight against their own decay. They suffer terribly, and there are cases where they become a drug addict, alcoholic, or even commit suicide. However, if they manage to gather enough strength and fight their way into really falling out of love, with God's help (atheist readers excuse me), they can see reality again, understand the monstrosity of which they were a victim, and unmask the person who oppressed their heart, giving them back the hell that they created. This time, though, they usually do it permanently for having a fact-based truth on their side.

\par All these emotional and mental hells are only possible because we make the mistake of taking manipulative women seriously, instead of seeing them as mere naughty children. A moment of distraction is enough to let us get swayed by conversations and lured into multiple negative states. If you take the nonsense of the female world that we are dealing with seriously, talking futility as if it was a serious and very important thing, you will be lost. You will soon be drawn to states of confusion, wrath, fury, sadness, doubt, etc.