\section{The Attraction for Cruelty}

\par Unfortunately, there exist masochistic women who seem to appreciate men who make them feel fear, because they think more or less the following: \enquote{If I fear this man, other people also do, so I will be safe. Moreover, other women will desire him and will be jealous of me.}

\par Such women feel safe around cruel men. They manage to \enquote{tame} him by means of sex and affection, until he becomes submissive to the point of being handled as they please, moment which, paradoxically, he is intended to perform the function of an emotional slave who provides and protects them. Cláudia Pacheco analyzes this point. In case the \enquote{taming} attempt fails, insistence lasts indefinitely under the guise of love and is followed by lamentations. On the other hand, such masochistic women feel incomplete when their partners are kind men. The test of reproductive, protective, and providing capacities is continuous and repeats periodically for as long as the relationship lasts, never leaving us alone.

\par Every male category serves a specific purpose in the life of certain women: kind men serve as emotional slaves who give them love without receiving it in return; working and rich men serve to give them money and financial support while getting cheated on in return; evil and cruel men serve to protect them; sleazebags, perverts, womanizers, and depraved men serve to give them intense sex, fulfilling their unconscious fantasies of prostitution\footnotemark[11]. Note that this last male category corresponds precisely to the kind of men who do not fall in love and get the best from them: limitless hot sex.

\footnotetext[11]{About this fantasy, read Eliana Calligaris.}

\par Men of unassailable character and higher principles, standard-bearers of values, are sometimes strongly flirted with by masochistic women, which makes them believe that they are sexually desired for being \enquote{superior males.} In actuality, they are mistaken: what happens is that they are desired for behaving as potential ideal husbands, should they be dominated and emotionally enslaved.

\par It is a shame: cruel and insensible men are seen as self-assured, whereas kind men are seen as weak.

\par When we decide to be monogamous and loyal to such a woman, she does not believe we do so deliberately, voluntarily, and on our own, but rather out of our incompetence in seducing other, more interesting females, or because we are shy. Husbands of unassailable character go through a lowering of standard by many women, including their own wives. These women are used to believe that we are loyal by incompetence, self-doubt, fear, and ineptitude in seducing other women, not because we want it. Loyal men are seen as shy, and not as valuable or honorable by such wives (which, obviously, they strictly deny, at the same time they fantasize stupid romances with artists, famous men, or powerful men, who are inevitably promiscuous). To make it worse, when we are satisfied with their physical condition, accepting them for what they are, not minding their extra pounds or other physical details, not looking for completion outside of our relationship, the dignity in this noble attitude is neither recognized nor reciprocated the same way, but, disgracefully, they conclude more or less the following: \enquote{He accepts me for what I am and does not demand anything more because he does not value himself. Thus, he is a second-rate man, since he does not want women who are better, prettier, more caring, and more educated than me.} Such a fact shows ingratitude. This problem is serious because we cannot fall into depravity, promiscuity, and degeneration to elevate the concept that they have of us. Therefore, the solution is to leave them wondering by creating a silent mystery around the matter of our loyalty.

\par Despite the prevailing hypocrisy that makes them say otherwise, we are valued by the number of females we attract. This means if this kind of partner does not feel the weight of rivalry with other females, she will not respect us. This problem is even more serious, given that we do not want to fall into promiscuity and depravity. Promiscuous men are harming themselves, even though everyone considers them very manly. The solution is to keep an element of mystery, talking little and preserving her doubt.

\par Irrespective of this fatal attraction that some women feel to perverse men, we must never satisfy it by shouting, and definitely not by assaulting them. The correct thing to do is to hit them by psychological mechanisms, reaching their feelings, just like they do to us. To do that, we must top them in all behavioral domains, being stronger and not letting ourselves be imposed on by their weaknesses. We must be, at the same time, more loving, more cold, more indifferent, more protective, more caring, more dedicated, more romantic, more insensible, more disconcerting, and more mysterious than they are to us.

\par Thus, if we want to master our relationship, we must be a synthesis of the many aforementioned categories, merging them into our personality, which is only possible when we dissolve the ego\footnotemark[12]. Above all, we must not fall in love.

\footnotetext[12]{\enquote{Dissolve the ego}: expression used by certain authors to designate assimilation of autonomous complexes or psychic aggregates which personify our mistakes, weaknesses, and debilities.}

\par Almost everything that we usually do to try to seduce them has the opposite effect. The only women who accept men who chase them, flatter them, sacrifice themselves, and go after them with flowers, letters, and other nonsense are the desperate ones: women who have no options. The other women prefer mysterious and indomitable men.

\par The preference that certain women have for the insincere, the worst, and rascal men is a proof of the prevalence of sexist values in their unconscious mind. Provoking a male to rejoice in seeing him enraged is a sexist attitude. Demanding being treated with indelicacy to get in line and behave honestly shows a sexist posture. Pushing a male over the edge, so that he makes extreme decisions, is a sign of sexism. Enjoying the adrenaline of fear is an indicator of a sexist posture. Thus, sexism is not exclusive to men and is rooted in the mind of masochistic women. Even among women who claim to be anti-sexist, we find a few who feel incomplete if they are together with a \enquote{wimp,} a kind man. Despite all is said otherwise, the fact is that they want real manly men who are truly masculine, and the undeniable existence of exceptions does not invalidate this hypothesis. And the reason for this is their instincts, which guide them in the direction of the satisfaction of their needs to be protected and leaded.

\par Transform yourself. Do the opposite of what everyone is doing. Counter her opinions, wreck her arguments without hesitation, but at the same time... confuse her by protecting and leading her. Do not offer passionate love; offer firmness, security, and determination, which correspond to true love. Take sex as something that is owed you, that you arguably deserve.