\section{The Thwarted Expectations}

\par The selfishness of devious women drives them to constantly make promises and break their words so as to enjoy our frustration. They spark our desires only to then wriggle out of satisfying them, for the purpose of keeping them alive. This way, they get a highly precise measure of our dependency and of their own seductive and attracting powers.

\par We dismantle this mechanism when we identify behaviors that raise expectations that would turn into frustration, and anticipate them by showing that we already know what they really hide. Before behaviors that promise us what we really want, we must not show enthusiasm but rather disappointment for knowing they are deceitful, mere empty promises.

\par A male's frustration gives such women a great satisfaction, because it reveals what we feel and provides them evidence that we value what they have to offer. We must not, thus, depend on what they can offer to be happy. Happiness must be sought within ourselves, which is really difficult.

\par Always keep an eye out on everything they promise. There exist two kinds of promise: explicit ones and implicit ones. Explicit promises are verbally articulated, whereas implicit promises are the worst, the kind that is glimpsed in attitudes and behaviors. Always expect the worst and stay vigilant. Always assume there are, behind an apparently promising, friendly, caring, loving, and seductive behavior, intentions to thwart and to deceive you.

\par Do not raise your level of expectation. Do not be fascinated by wonderful opportunities you envision. Keep your expectation level at zero. Do not expect anything and, at the same time, expect everything. Be extremely realistic. Do not let illusions snatch you out of reality. See it as it is.

\par We can fight empty promises in two cases or instances: the moment they are developing and after they have already thwarted us.

\par If you stay vigilant, you can fight a trick by thwarting a devious woman before she thwarts you. The ideal moment for this is when a promise is developing, being made. In order to thwart it, just communicate that you will be watching her to confirm if she is really going to honor what she says. In case of recurrence of a same thwarting promise, inform her a second time that you already know this is a lie. Show little or no expectation, make it visible. Let her know in advance in the good times that you already know what is coming.

\par If you are being treated well, flirted with, or welcomed, get ready for a surprise because out of a sudden something unpleasant will happen. For instance, it is common to have meetings arranged excitedly, and, in the day of the meeting, a devious woman to treat you coldly, to stay quiet, to bring a male friend, a female friend, or a child along with her, to not show up, etc.

\par However, if you failed to stay vigilant and fell into one such psychological trap, unmask her, establish a \enquote{punishment}\footnotemark[13] as a consequence for the next time this happens, and inform it to her without leaving any room for an argument. This way, you will render her powerless and will lead her to a dead end, making it impossible for her to thwart you for as long as the possibility of carrying out the \enquote{punishment} lasts. Truth will be on your side and can be used against the manipulative woman, who will have been defeated the moment she feels unmasked. As long as the \enquote{little punishment} is pending, funny business will be suspended. If it is your first date and you are not closely acquainted with her, by the time you smell a treacherous change of behavior, simply get ahead of it and become silent, while constantly staring at her eyes calmly and coldly all the time, and saying sound things that disconcert her.

\footnotetext[13]{I refer to returning the consequences of insincere actions.}

\par A \enquote{punishment} that usually gives results is to be real quiet, to stop talking, and not to say a thing or to say the least you can in \enquote{retaliation} to an unpleasant fact. This is a good \enquote{little punishment,} but must always be used with a fair criterion and in the right context to give results. You must be fair, even if she has not been.

\par It is very dangerous to deal with such \enquote{little punishments.} Every undesirable conduct requires a specific reaction that must be correctly established, with evident flawless justice. The slightest injustice can be fatal to us, because it proves them right, and thus gives them cause to safely retaliate us, since we will be wrong and who is wrong can never protest. A slight clerical error or a mere inattention is enough to have the opposite of the intended effect. Obviously, it is a must not to be in love in order to perform such maneuvers. If we are in love, this will blow up in our face.

\par Through psychological discipline, be ready to react correctly and justly. The moments when we are more exposed to be hoodwinked by manipulative women are the ones when we are being treated well, when there are no fights and the relationship is going well. We tend to let our guard down at such times, and they, instead of reciprocating the noble act of trust as a virtuous woman would, take this opportunity to hit us off-guard, which proves that they have a malign treacherous nature and are selfish.