\section{How Not to Fall in Love}

\par A man's passion can be defined as an hypnotic fascination for a woman's voice, delicacy, beauty, scent, touch, caress, softness, whisper, and fragility. It is most felt in abstinence periods.

\par A woman's fascinating characteristics attract us, tie us up, intoxicate us, blow us away, and drive us mad. They subject us, degrading us to the level of a doormat with no honor or self-respect. Like a drug, they cloud our judgment and prevent us from thinking clearly.

\par In such a condition, we become exactly the opposite of the dominant masculine model that would make them giddy with passion, which always gives us the opposite of the desired result. We become submissive, dependent on their love being granted to us so that we can enjoy a few minutes of happiness. We see the woman as a lifeline to ours sorrows. Passion is a form of dementia.

\par In order to protect ourselves from this danger and get rid of this emotional sickness once it is in place, we need to correctly employ willpower, spiritual discipline, and mental discipline. It is not by chance that many spiritualistic ascetics have avoided women and sex. The hell of passion is really unbearable and only a few do triumph over it.

\par The first thing you need to do is to learn how to rule your mind, avoiding mechanical imagination. All of the good and bad mental images related to the object of passion (the goddess in our dreams) need to be suppressed by means of willpower. Those that cannot be stopped must be analyzed. It is necessary to reach mental silence. We must also work on the death of psychic aggregates involved in romantic fascination.

\par The more feminine a woman is, the more fascinating and potentially dangerous she will be. We must, from the beginning of our relationship, resist the fascination, fight the memories, fantasies, and thoughts related to such a passionate love. It is the charm of Lilith-Nahemah\footnotemark[14] that misleads the innocent to the abyss. Woe to the innocent and weak who are mesmerized by the charm of Circe, Delilah, and Helen of Troy\footnotemark[15]! They will dive into the abyss upside down, like an inverted pentacle. Woe to those who believe in earthly happiness and seek them outside of themselves, in passionate love, because they will only find suffering and madness there.

\footnotetext[14]{In certain branches of Hebraic mythology, it was Lilith and Nahemah, not Eve, who led Adam astray.}

\footnotetext[15]{Mythological representations of simultaneously fascinating, beautiful, and perverse women.}

\par Due to its very absurd fatal logic, female passionate love\footnotemark[16] is doomed to eternal dissatisfaction, since it inherently has as its selective criterion masculine indifference and aloofness. This means that whenever we desire a woman's love, it will run away from us, and will only come to meet us when we do not want it, when we reject it\footnotemark[17]. There is no way to simulate it by faking indifference, because the unconscious expresses the actual content of our feelings by subliminal means.

\footnotetext[16]{Note that I refer here to a woman's passionate love, not her conscious sober love, nor a man's insane passionate fatal love.}

\footnotetext[17]{A similar thing happens to women: a man's love only comes to her when she doesn't want it. This fatality prevents people from being happy in passionate love, since it pushes them to the direction of those who don't love them.}

\par Passion is a set of defects we carry in our soul, in our psyche. In order to overcome it, it must be previously understood through self-analysis.

\par The analysis of passion is performed by gathering as much information as possible about feelings, thoughts, and actions related to it. It is not theoretical but rather practical. To theorize about a psychological element is to break away from understanding it by making up hypothetical ideas about its properties. Information is first gathered through self-observation in the moments that passion is manifested, that is, it is a self-study on the spot. No theorizing must be accepted. All details of the movements, thoughts, and feelings are important and must be gathered. In serious cases, one can supplement the work with a self-analysis subsequent to the manifestation, but based exclusively on observed and remembered facts, without theorizing and hypothesizing. Information about passion is present in the moment of its manifestation and can be gathered if we stay vigilant.

\par Passion is expressed in our minds in the form of multiple mental imagery: thoughts, memories, recollections, fantasies, and plans. At this level, it is an automatic mechanic autonomous imagination that does not obey our willpower. We can repel it and it will come right back.

\par Besides our mind, danger is present in our heart in the form of feelings, which are strictly tied to the mental imagery that exists in our head. It is felt as blows that actually hurt. The feelings that comprise passion are longing, jealousy, the joy of being together, and many others that we cannot list here due to lack of space. At this level, it gets subtle and blends in very much.

\par At the level of body movements, we can catch a passionate weakness when we turn our head or eyes to contemplate the loved person, when we reach out and give them a call, when we talk towards them, and in countless other movements that vary from case to case and person to person.

\par We can also observe and study passion as sexual and instinctual manifestations. As an instinct, that is, as everything that relates to the preservation of species and of oneself, we can see it increasing our heart rate, respiration rate, reducing hunger, etc.

\par The pain of lovesickness is real, excruciating, and deep. It is felt clearly in the heart and detectable in an objective manner. It causes visible and indisputable damages.

\par Some people say that we must adore women. This is something controversial. An authentic woman who has fought herself, engendered her soul, and defeated her low instincts is really worth of veneration; she must be taken care of as a gem, protected, and rewarded. On the other hand, a mere treacherous devious woman does not deserve the same \enquote{adoration,} since she is not less mean than anyone, despite having an angelical fragile appearance.

\par The more you think (well or badly) of a devious woman, the worse it is. The ideal thing is to simply forget her and give no importance to your own whims, feelings, desires, thoughts, and absurd fantasies. Do not ever take her seriously; stay aloof and mysterious.

\par If you \enquote{drink the poison} of passion\footnotemark[18], the spell will conduct your thoughts by force in an autonomous manner. You will try to think about other people, but you will not be able to. Your beloved will dwell in your dreams, your imagination, and your mind against your will. She will be an intruder in your heart. You will try to divert the attention from her, but whenever you do it, you will repeat the cycle and will be again paying attention, thinking and worrying about the witch. You will not be able to ignore her.

\footnotetext[18]{The \enquote{poison} is drank by means of credulity. When we put skepticism aside and indulge in it, from that moment on we are intoxicated. It's much easier to prevent passion from settling in than it is to rip it out of our heart once it has settled.}

\par Nevertheless, she is not your enemy: your enemy is yourself. It is against yourself that you must fight: against your weaknesses, follies, affections, desires, longings, dreams, fantasies, sorrows, attachments, etc. A man's worst enemy is himself. When we overcome ourselves, we overcome devious women by extension, because, ultimately, they are not the ones who strike us and hurt us, but rather our own feelings. Our partners only use our weaknesses against us, and by doing it, they are really showing us who we are and, in a way, helping us. Thus, do not rebel against anyone, let alone against women, because it is utterly a waste of time and nobody will care. Rebelling against women is nonsense.

\par Be aware of the addiction to find that she looks like your mother. The tendency to see a partner as one's mother is one of the roots for falling in love. It is the same feeling we had in our childhood that makes us see them as lifelines.

\par The procedure to be cured from passion is the same by which any sickness of the soul is cured: understanding.