\section{\enquote{Cornering} Decisions}

\par In order to render them powerless and prevent them from playing with our noble feelings, we need to make sound decisions. Sound decisions are those that turn the tide in our favor, keeping truth on our side, and force them to act in a transparent manner, revealing what they truly feel.

\par We can say that the overriding strategy in such emotional defensive maneuvers consists of creating objective, decisive, radical, and \enquote{cornering} conditions which a devious woman cannot escape from and which forces her to reveal what she truly wants and feels towards us, since dissimulation, uncertainty, and deception are her main psychological ruses. They try to hide what they truly feel, desire, and want to throw us off. They hide their true intentions and simulate false intentions to mislead us. \textit{\enquote{Cornering} decisions} must be understood and defined this way: brave unquestionable attitudes that leave a woman no other choice than revealing in an unequivocal manner her truly intentions toward us. They are attitudes requiring total detachment and dispassion, without which this would violently backfire onto us. It is necessary to be truly prepared to lose her forever for such a radical strategy to work. Thus, do not try such a maneuver if you are in love, attached, or not prepared to really risk losing her. By means of \enquote{cornering} decisions, which I will describe in a moment, you will know what lurks inside a confusing bewildering behavior. Once you have learned the truth, it will be a lot easier to decide what to do with your life and what should be done with your relationship with your scheming woman.

\par First of all, do not make idle threats by making promises that you cannot fulfill, because if you do it, your credibility will be lost and your threats of breaking up with her, dumping her for another woman, never seeking her again, etc. will look ridiculous\footnotemark[19]. They usually play to the utmost limits to find out if we are bluffing.

\footnotetext[19]{This is the very funny case of a man who says he will \enquote{punish} a woman with his absence, but can never fulfill his words.}

\par Some \enquote{cornering} and \enquote{punitive} decisions such as the following may help:
\begin{itemize}
	\item Leaving her for a while so she suffers enough;
	\item Being quiet, reducing the conversation to zero or almost zero;
	\item Establishing consequences (end of the relationship, involvement with another woman, definitive break of contact, end of the commitment, etc.) for the next time that an undesirable behavior happens again.
\end{itemize}

\par \enquote{Cornering} and \enquote{punitive} decisions can be expressed in several ways, but typically, they must contain an anticipating component (\enquote{next time you do that}) and a feedback consequence that is morally on par and corresponds to the undesirable behavior that originates it.

\par When your girlfriend or wife stays long periods without giving you a call and then come up with a poor excuse, keep your mouth shut and do not talk until she insists in knowing what is going on. Then, tell her you will only talk to her again the day she commits herself to call you with the frequency of a woman who loves. Apply the same method to long absences or situations when you get confused, not knowing with whom she is or what she is doing.

\par If your female partner likes to keep her phone turned off to make your life hell with doubt, inform her that you will only accept her calls again when she commits to keep her phone permanently turned on.

\par If your partner likes to refuse sex by alleging absurd reasons, or if she unwillingly, half-heartedly gives herself to you, forbid her from seeking you again while she is not filled with burning desire, and inform her that you will only accept her again when she commits to always have sex with burning desire, in the form and frequency that you need, no frills.

\par If your female partner insists in offering but not in giving, in promising but not in fulfilling, get some distance from her and inform her that you will only resume contact with her the day she corrects herself.

\par If your girlfriend treats \enquote{harmless} men in a suspicious manner that disturbs you, unmask her by bluntly pointing out the suspicious behavior that disturbed you and inform her that the next time this happens again, you will dump her for another woman immediately. The technique of getting some distance and demanding a correction of her behavior for resuming contact also work in these cases.

\par If your girl insists in exonerating forgiving attitudes and strictly refuses to recognize the malicious ulterior motives of the men who surround her, or persists in being unnecessarily thoughtful, excessively nice and friendly with \enquote{good} guys\footnotemark[20], while giving poor excuses, tell her to seek you again only the day she changes her mind and recognizes her mistake.

\footnotetext[20]{It's very commonly known this ruse of phony good men who actually want to bed her.}

\par Do not be afraid. If she truly loves you, she will end up agreeing. If she does not, it is because she never actually loved you and nothing was lost. Either way, truth will come out and will put all doubts and uncertainties to rest.

\par Before your female suddenly disappears without a word, as devious women usually do to make us desperate of love, inform her that if she stays absent for more than two or three days without giving any explanations, you will simply conclude that \textbf{she} decided to call it quits. They like to do this to make us worry and imagine that something serious happened to them, that maybe somebody kidnapped them, or simply that they are in a love hotel with someone else!

\par In short, if your partner behaves in an improper way, withholds sex, avoids kisses and hugs, mistreats you, avoids you, provokes you, challenges you, annoys you, thwarts you, does not call you, is being arrogant, etc., simply halt the relationship by suddenly getting distant and totally shutting yourself down. Do not flirt with her, do not seek her for sex, do not talk to her, do not call her, do not question her, do not force her into saying what is going on, and, above all, keep your head cool, preserve your coldness, and do not fight, do not fight, do not fight! Break contact with her and wait, wait, wait, and wait. Endure it to the end and do not give in to her (which is why we must never fall in love). There will be a moment in which she will not endure the emotional stress that she herself created and will come to you to know what is happening, because doubt and curiosity will be engulfing her alive. Then, impose your conditions with no excuses, make the correct and necessary demands for resuming the relationship: frequency and quality of sex\footnotemark[21], frequency of calls and dates, the right way to be treated, exclusivity of her attention, getting distance from flirtatious men in disguise, etc.

\footnotetext[21]{If she has had sexual intercourse before. It would be dishonest to use this mechanism to force her to have sex with us if she has never had it before. I refer to the preservation and the improvement of the frequency and quality of sex that one already has had.}

\par You must formulate your requirements in a totally clear manner in order to prevent the customary pretenses of misunderstanding. Obviously, you must be polite, calm, and lovely, but, at the same time, straightforward, decisive, realistic, and crude.

\par You must rigorously honor all the above-mentioned retaliating promises. Do not make a threat that you cannot back up. However, do not try to do any of that if you are in love or attached, because the one getting struck dead will be you.

\par Your decisions must eliminate all possibilities of dissimulation and deceit, while leading to only one result: revelation. For this purpose, they must have only two options or ways out for a devious woman: meeting your demands or ending the relationship. If she loves you, she will do what you demand (and you must demand something fair, otherwise your girlfriend will feel wronged and will seek revenge for a good reason; always keep truth on your side). If she prefers to end the relationship, it is because she never loved you and she was no good to you anyway, so she will not be missed.

\par Once this evil and treacherous nature of many female animals is understood, as well as the impossibility of us falling in love without suffering bad consequences, it inevitably arises in the masculine mind the following question: Will we have to give up the idea of having a partner? How to put a woman inside our house and live with her under the same roof?

\par To solve this problem, it seems to me that the most viable solution is to keep temporary relationships, without the lifelong commitments of the paper\footnotemark[22], extended by the time that our partner provides certainty of loyalty, honesty, and transparency\footnotemark[23]. When this certainty is irreparably shaken\footnotemark[24], this means that it is time to try a new venture. A suspicion, even tenuous\footnotemark[25], of betrayal or cheating, if not undone, is enough to define the total rupture of emotional commitment without appeal. It is not necessary to wait for certainty. A serious mistake that I notice in many suffering men consists precisely of waiting to know for sure that they are being cheated on by their partners, only then to break up the relationship or, at least, end up the commitment, instead of giving them back the consequences at the first sneaking suspicion. Such a weakness comes from falling in love. If we stay dispassionate, we will not have to wait for the moment that we catch them naked with their lovers; detecting lies, inconsistencies, or simply something poorly explained will suffice for us to decree the end of commitment. Inform her, without arguing, that at the first sign of something wrong, consequences will return to her.

\footnotetext[22]{There just aren't women like there used to be anymore.}

\footnotetext[23]{This way, the running time of the relationship will be in the hands of your partner, who will define it with her behavior. If she wants to preserve her husband on her side forever, she will have to keep to the straight and narrow.}

\footnotetext[24]{By proven lies and deceiving attempts. For instance, telling her husband she is going to a birthday party, but she is not there when he calls her.}

\footnotetext[25]{I refer to tenuous suspicions but which are serious and based on unequivocal facts.}

%TODO "intested man in disguise" or something else?
\par There are large and small betrayals. Small betrayals are subtle and very frequent, often disguised under a sentimental justification that makes them look innocent and sublime. Examples of subtle betrayals are: lying, accepting needless wooing of other men, being friendly and caring with males who desire her, etc. Their poor excuses are always the same: they claim that they feel sorry for the \enquote{poor thing,} that he has no \enquote{bad intentions,} or that they have not noticed his ulterior motives, etc. In actuality, what they really want is to preserve the desires and hopes of the interested man in disguise by avoiding cutting him off and pushing him away.

\par Obviously, the partner must have been previously informed about behaviors that cause distrust and bring an end to the commitment, so that she does not have deniability and accuse you of injustice. Draw up a list of suspicious behaviors that bother you (obviously, do not be absurd, make a cold and reasonable judgment) and notify her in a decisive manner. If she has been previously warned and feels certainty in your voice and your gaze, she will stay longer trying to look loyal and will prolong the relationship, perhaps indefinitely. But she must always be kept \enquote{on a tightrope.} What is the purpose of all this? To try to revive the almost extinct role of wife, practically non-existent in our days.

\par The inferior male emotional intelligence has made men less manipulative and more vulnerable to the effects of emotional attacks. Throughout history, men were never able to respond to emotional attacks with equally emotional responses. Stupidly, they always responded it with physical reactions, which has made them wrong and allowed countless accusations, besides nurturing an ancestral unconscious hatred against females. As women were never hit back in their feelings by their mind games, pestering acts, manipulation, deceit, etc., devious women believe that they are invulnerable in this field, and seldom suffer the pain that we feel. We do not fight back the same way, but in a different way, and this is our mistake. In addition to serving as a proof of cowardice and weakness, the acts of assaulting them physically, insulting, cursing, yelling, etc. are a harmful waste of time that, in the long run, favor them and allow them to play the victim. Thus, we must learn to hit them back in their feelings, so that they know what it feels like to have their most noble feelings turned into objects of irresponsible jokes. Joking with feelings and abusing one's sincerity is almost the same as playing with life\footnotemark[26]. Unfortunately, most men are too weak to return them the appropriate emotional consequences. If such consequences always came, certainly the employment of ruses would decrease.

\footnotetext[26]{A proof of that is the fit of furious madness of betrayed husbands and ex-husbands who kidnap their family and kill themselves. Male passion has its own fatal side that can never be overlooked. Guarding people against it is to do good.}

\par Applying \enquote{cornering} decisions is much better than wasting time on discussions in a foolish attempt of forcing them to admit their mistakes, which always has the opposite effect.