\section{The Importance of Not Becoming Polarized}

\par We can define the ability of dealing with women as the art of properly managing our good deeds and the so-called \enquote{bad deeds}\footnotemark[27] at appropriate times.

\footnotetext[27]{Only under a certain female perspective. It is in this sense that women perceive as \enquote{bad} a man who doesn't allow himself to be manipulated and returns fair consequences to their actions. It must be understood that the words \enquote{bad} and \enquote{cruel} are used here as a figure of speech, not to designate harmful deeds toward others. The concepts of \enquote{good} and \enquote{bad} always cause confusion and polemics, because good and bad is relative. What a devious shrew deems \enquote{bad} is seen differently by a righteous woman. Thus, becoming distant, not giving a call, staying quiet, and unmasking lies are considered bad deeds by many people, even if such people are arrogant, cold, distant, unclear, and indifferent toward us.}

\par If we are exclusively good, we will be perceived as fools and will be deceived. If we are exclusively bad, in the broadest sense, we will be wrong, lose our minds, and give them ground to take revenge in all fairness. The ideal thing is to be simultaneously good and, in a way, \enquote{bad,} loving, and a bit \enquote{cruel,} depending on the situation, without ever becoming polarized to any side.

\par Always keep truth on your side and never be unfair. This way, you can unmask their mistakes and dishonesty, destroying their defenses.

\par Act as if you are taming her\footnotemark[28]. Reward honesty, transparency, and loyalty with some cuddling, gifts, dedication, and protection. On the other hand, do not be afraid when you need to \enquote{punish}\footnotemark[29] dishonesty, suspicious ambiguous confusing behaviors, and subtle betrayals. If she is truly regretful for actions that are not serious, what tends to be rare since pretenses are often observed in females, be understanding. Watch out for crocodile tears.

\footnotetext[28]{Many books have been written teaching women how to do this to men. Read about this subject in Karen Salmansohn and Amy Sutherland.}

\footnotetext[29]{With the mirroring and feedback actions of boycotting, as already mentioned.}

\par You must adapt appropriately to different situations, without sticking to the good side or the (according to them) \enquote{bad} side. Do not be exclusively good or bad; disconcert her. Be fair. Never punish her without her deserving it, because this legitimizes resentment. If you mess up, hurry up and fix your mistake.

\par Make her get used to your presence and not your absence. If you distance yourself too often, your partner will get used to your absence and your plan will go down the drain. On the other hand, if you are always present, you will not be valued. The ideal thing is to distance yourself or break off contact only at the right times, that is, when there is a deceiving attempt. However, in these moments, the isolation must be prolonged and complete. Do not waste the time that you accumulated on the resistance: if you have endured two days without calling her or seeking her, you will waste this time if you get weak in the third day, and will have to start the countdown all over again.

\par It is always necessary to compensate your harshness with protection and honest caring. Continuous coldness and distancing make the relationship grow cold.

\par Beginners are often fixated on goodness or badness, and always get the opposite of the expected results, and that is why this book is intended not only for seasoned people. To master your relationship, it is necessary to fluctuate according to requirements imposed on by female games and to keep yourself above their mediocrity and futility, a skill that requires a radical death of our defects and weaknesses.
