\section{The danger of taking it the wrong way}

\par None of the observations, recommendations, suggestions, and thoughts contained in my books must be taken dogmatically and without criticism. I do not write for ignorant people who look for ready formulas and finished, closed ideas. I only provide a provisional model for better understanding of the contradictions which we come across in love.

\par The messages that I have received show that many readers have not understood the need to balance out opposite attitudes in appropriate doses and according to the circumstances. By being informed that they need to return strength, security, and firmness, they have made the mistake of becoming polarized exclusively in distancing and indifference, which gave them a disastrous effect.

\par The most sensitive men, who had bitter experiences, concluded that they should simply become the opposite of what they had been, and later complained about lack of results, but they have not taken the responsibility for themselves as they should.

\par It turns out that dealing with women is not as easy as unaware men assume. It is not enough to take the stance of an one-sided tough guy and that is it. Much more is necessary: to know how to reward her good behaviors, to reciprocate her sincerity, to have firm, protective attitudes, to have malleability, to alternate your behavior, to be able to accept, to be adaptable, etc.

\par A point that caused misunderstanding was the one about rejection. We must not reject a woman when she comes to us and offer herself sincerely, but rather to enjoy the opportunity and reciprocate it. We must only reject her when we notice indicators of a trap, shrewdness, or emotional deceit, such as, for instance, when she offers herself to attract us in order to then despise us or replace us. While we are not seeing such indicators, we must accept her approaches and enjoy it. However, when we notice that a devious woman is trying to pull a chased one on us, we need to be faster and reject her, or to \enquote{scold} her first, thus stealing the feeling of triumph from her and \enquote{shocking her.}

\par It is not advisable to push her away senselessly, without a criterion and in a random way, but only when we sense the smell of an irresponsible game, of her attracting and rejecting game. In cases where she is giving signals that are explicitly conducive to approaching, the correct thing to do is to take the opportunity and approach her, welcoming it, but without fully letting our guard down.

\par At the root of the mistakes that I am pointing out are the belief that it would suffice to replace a certain behavioral conditioning with another and also the conviction that there are general rules that can be mechanically applied to all situations. There is no such a thing. Female psyche is complex and the behavioral and analytic parameters that I provide are only guiding principles, which are effective only when dosed and adapted in a contextualized way. Therefore, men who do not know how to identify situations to apply them correctly will get results opposite to the expected. A same action may take multiple effects according to different situations or contexts. Men who think that there is a set of ready-made recipes that will always work in all situations, regardless of when it is applied, are nowhere close to understanding this science and they would do better if they gave up on it. Dealing with women is not for unaware, stupid, misogynous, moronic men endowed with little intelligence.

\par One of our fundamental mistakes consists of us not accepting the cold, selfish, indifferent nature of women with respect to us. We insist on not accepting reality and on nourishing the absurd hope that women may offer their love to men who request it. Against all evidence, we strongly deny to ourselves the undeniable fact that female love is offered only to men who do not want it or while we are not wanting it. This refusal to surrender ourselves to reality is the cause of our torment.

\par It follows, thus, that our fight is against ourselves, against the obsession of our absurd illusions, dreams, and hopes, and not against the opposite gender, as some men who wrote me believe. It is a waste of time setting ourselves against women. Attempting to force them to change their behavior is pointless. Passion is our great enemy. Our need to be loved by the women whom we love kills us.\footnotemark[2]

\footnotetext[2]{For being exaggeratedly intense in men. If it was something sober, it would be good, but a man's need to be loved by a woman is usually exaggerated in our Western culture, due to ideological fixations started in childhood and violently reinforced in adolescence. Women seem to me more balanced in this respect, and that's precisely why they dominate men, not always in an altruistic way.}

\par We must work on our inside in the sense of accepting reality, even if it is painful. Reality will not change, will not submit to our desires. Human females will not stop being what they are and what they were. Thus, we must eliminate our desires for them to be consistent, logical, and sensible\footnotemark[3] in love and in sex.

\footnotetext[3]{From men's standpoint.}

\par Note that women do not accept that we are humans. This happens because they want to give themselves to a \enquote{Beyond Man.} When they find out that the man whom they have by their side is a human, who suffers and feels, they get mad instead of having compassion. Be aware that your emotional suffering will make her irritated instead of make her feel compassion. It is almost impossible for women to feel compassion for the emotional suffering of one who was supposed to be her man. For this reason, if you request to be loved, it is more likely that you will provoke her revulsion than her pity.

\par Loving who does not love us and feeling aversion for who loves us is illogical. However, female unconscious follows its own principles, and ladies, usually, do not control it, do not confront it, and, oftentimes, do not even suspect that it exists\footnotemark[4]. Thus, we are the ones who have to study them, to observe them, to understand them, to comprehend them, and to accept them, because they will hardly be able to do it to us. But this understanding will not be possible while we are being driven mad by passion.

\footnotetext[4]{When a person, whether a woman or a man, admits that they have an obscure side, they start to observe and understand it, transcending themselves and becoming happier.}

\par When we are in love, we want to be loved by females, we want them to be together with us all the time, as in a continuous sexual union. This continuous request of contact causes aversion. The worst thing is that they are the ones who request and call in passion from us, but when we give them that, they reject us and proceed to avoid us.

\par Every time a man tries to live a \enquote{great love,}\footnotemark[5] a terrible disgrace befalls him. Passionate love is very close to hatred for being irrational, instinctive, and animal. This is why both forms of passion usually follow each other.\footnotemark[6]

\footnotetext[5]{I refer to passionate-romantic love, which is insane and it's nothing but a sentimental disguise of brute animal instinct, and not to altruistic true love.}

\footnotetext[6]{This is one of the many reasons why I don't write for men who indulges in negative feelings. Hatred and resentment worsen a man's condition, they make him sick.}

\par There is, thus, no way other than dissolving in your heart all shadows of attachment, passion, and sentimentality\footnotemark[7].

\footnotetext[7]{This will not transform us into monsters, but, instead, will allow the unfolding of sublime and superior internal states. I insist so much in the dissolution of sentimentality for it being dangerous, given its immense magnetic hypnotic power to seduce and to fool, while passing as something sublime and spiritual.}

\par If you are suffering for any devious woman, you can die and you will arouse no pity in her. You will be seen as a weak, useless, worthless man who is unable to take care of himself, [...] Therefore, do not waste your time suffering for any \enquote{bitch.}\footnotemark[8] Love yourself and do not dream with hypocritical ridiculous romances. The danger and falsehood of rosy love exist in a direct proportion of its beauty and fascination. Learn how to resist what is beautiful, wonderful, and fascinating.

\footnotetext[8]{By \enquote{bitch} I mean an idle shrew who spends her time playing with what is most serious to a man: his sincere feelings. Not all women do this, though. I have met women who, for being able to deal very well with their obscure side instead of denying it, they do not make bad jokes with a man's love.}

\par First of all, let us remember that we will die and will be forgotten. Therefore, let us seek happiness inside our soul and not outside. Let us give ourselves to our Spirit. Only He will be with us after our death.

\par Your partner will be less cold if she believes that you are \enquote{the deal,} \enquote{the man,} \enquote{the greatest,} but she will never love you like you would like, that is, simply for what you are: a human being who suffers and feels. Above all, she will not feel tenderness toward you. She will complain nonstop, but the interesting results will make themselves felt.

\par Do not simply treat her with coldness and indifference: be her mirror most of the time. Say you love her only when she says it, give her gifts when you receive them, but be distant when she is being cold. Reciprocate what you receive in the same way. If you receive caress, reciprocate it (not much). If you receive coldness, reciprocate it with coldness. If she avoids you, unmask her and avoid her. If she complains about all this, rub it in her face. This requires dispassion and behavioral deconditioning. Give it as good as you get it, and, sometimes, even more intensely than you get it. Tame her.\footnotemark[9] However, have your foothold in masculinity: be more \enquote{fearsome} than loving, colder than affectionate, more \enquote{cruel} than merciful, more distant than close. Still, be mysterious, protective, and leading. Obviously, never fail to exhaust her with intense sex.

\footnotetext[9]{Isn't that what Karen Salmansohn and Amy Sutherland suggest all the time, which is why they are applauded?}

\par Let us see now some ill-intended skewing. Some dumbasses said that my books encourage male promiscuity. This is a lie. What I do is to denounce female preference for promiscuous men. In fact, I am against promiscuity and sexual degeneration. If any time I wrote that women build sociopsychological structures that corner a man and push him toward promiscuity, I did it in a denouncing way so that the ruse was torn apart. Moreover, a man who knows female psyche and is able to tie a woman to himself whom he finds interesting and with whom he has great affinity, he will be much more satisfied and will be less inclined to promiscuity and changing partner.

\par According to other dumbasses, I am attacking women and, therefore, this is evidence that we, scholars of male loving crises and female ruses, appreciate neither women nor sex. This is another slanderous deceit. What we teach is precisely how to win women over in the war of passion so that we get what we are refused: certainty, resolution, clarity, and transparency in love and in sex. Obviously, one would not seek such elements in romantic relationships if they did not like the best that women have to offer. However, when we identify with these three attractive attributes and start to chase them like crazy, we lose them. Thus, in order to have them, we must first not desire them.

\par Some morons say that I am just an angry man trying to defame women, and they do this because it is the handiest conclusion that their deteriorated brains can achieve. Their short imagination does not allow them to conclude that there can be higher motivations for somebody who unveils bad intentions and romantic shrewdness. In the case of this ridiculous accusation that I am unmasking now, what logical dissection reveals is, beside their pure simple stupidity, their naive attempt of defensive manipulation against truths whose revelation and demonstration bother. The background thought with which these manipulative people work is that men cannot criticize female attitude nor protect themselves from psychological ruses that destroy honesty in relationships. In short, they fallaciously argue that we should stay passive before female cleverness because such a passivity would be, according to them, a proof that we like females.\footnotemark[10] They want to induce the following belief in unwary men: that it is impossible to find defects in something delicious. They suggest that, when we like something, we do not criticize it, and when we do not like something, we criticize it, that is, they stand for irrationality. They hide that delicious females have developed sophisticated ruses to outwit us and not give us their treasures (sex, affection, and love). In reality, what happens is the exact opposite of what these dumbasses preach: it is females who are indifferent and do not like men much, while we, males, desire, want, and love them desperately. All we need is to look around us a little, and we will see women disposing of men, saying that men are good for nothing and that they are not needed. The opposite never happens and has never happened. It has never been known that men wanted to build a society without women or to ban them from Earth, but this is precisely the speech of many women, feminists included. We know very well that we cannot live without women and we admit such a fact\footnotemark[11], whereas women usually take the opposite stance.

\footnotetext[10]{Every person, whether a man or a woman, has the right to defend themselves against romantic deception, but does not have the right to deceive.}

\footnotetext[11]{}

\par There are also resentful misogynists, who cannot bear reading any book without falling further deeper into their unhealthy negative emotional states. Well, if they are unhealthy, why do they seek philosophy? They should get healed first. This category of sick men believe that every book that falls into their hands is a support for their absurd worldview. Delusional, they see in sentences only confirmations of their unrealistic ideas.

\par I cannot forget to mention a category of asses (both male and female) who reacted with the ridiculous statement or assumption that we defend extreme violent sexism and oppression against women.\footnotemark[12] Such ignorant people show that they do not even know to read properly, because if they did, they would have noticed that the object of our criticism is precisely female behavior developed throughout history as manipulative adaptation, defensive and/or offensive, to unenlightened, extreme sexism. Such behavioral adaptations, conscious and unconscious ones, operate in the opposite side of the goal of men whom would supposedly wish well of the \enquote{fragile gender}, because they block the development of women as human beings. Does anyone believe that by manipulating, deceiving, and behaving childishly in love, would anyone reach happiness? Or that women's preference for the worst men benefit them in any respect? It turns out that people with the brain of a cockroach react to reading in a mere passionate emotional way, believing in the absurd that we benefit someone when we exempt them from criticism. They shrewdly imply that women should not be criticized for their deceit and shrewdness. They work with the background idea that criticism is harmful and never beneficial. They hide that women's adaptive behavior to retrograde extreme sexism has staunched women's evolution, harming them by transforming them, with a few exceptions, into superficial, futile, lying, passionate, irrational, manipulative, masochistic creatures, etc. They also hide the unconscious sexism rooted in female psyche, which drive them to continuously request to be dominated, subdued, leaded, to rate men by our hierarchical position, to get bored of democratic, good husbands, to prefer oppressive and rich men, etc. I defend, yes, an enlightened, tolerating, and conscious sexism. We could go against sexism itself because we would be going against ourselves. The expression \enquote{sexism} comes from the word sex and does not inherently imply oppression, exploitation, or violence, as dogmatic feminists try, purposefully, to make it look like in order to confuse people and induce them to conclude that males are naturally mean, violent, oppressive, and dangerous.

\footnotetext[12]{}

\par The three accusations above are sophistry. What is a sophism? They are arguments that have the purposeful intention of fooling unwary people by manipulating ideas such that logical mistakes are hidden. Sophistry is the main weapon of charlatans, rogues, and manipulators who are on the side of lies and exploitation of the other by inducing beliefs and feelings. We must dissect them and expose all their fallacious procedures to the sanitizing light of consciousness. Unfortunately, they will come back and continue disturbing the lives of sincere people, because it seems to me that dishonest behavior in the analysis is archetypical. It exists since Ancient Greece, and is today more active than never.