\section{Why don't women look at you?}

\par It bothers us to notice that we constantly look at women on the street, insanely desiring them, and they do not care at all for us, they ignore us. Why does this happen?

\par The answer is that nature has made females indifferent to males, and has made males desperate for females. Female sexual desire is much less intense than male desire.

\par Note that a human female can only be impregnated by one male in a period of a year. In contrast, how many females can a male impregnate in the same period?

\par If you withhold sex, you will see that your partner will only be affected after a few weeks. And even then, this will not be a result of the lack of sex itself but rather by a disturbance of the doubt about what is happening.

\par Women who show themselves as femme fatal are actually pretending. Even nymphoniacs, prostitutes, and porn actresses are not moved by mere genital desire as unaware men think. They're driven to the act by other reasons: money, acceptance, impaired self-esteem, competition, curiosity, etc. They get used to sexual hyperactivity and accept it, embodying it as a play. I want you to know that women don't like much sex per se and fool you. There are inorgasmic women who are extremely promiscuous.

\par There are many women who are proud of their inorgasmia. There are many women who affirm in so many words that they do not need men for anything. There are practically no cases of women who rape men, and you do not hear about women sexually harassing their children or brothers. We do not see women groping our manhood without us authorizing it when we are in a bus or in the street. I have never heard of a woman spying a man while he is showering. There are no proven cases of women waging war against other nations to take their men. However, the reverse is very well known since time immemorial. Such facts prove, in a totally undeniable manner, that female sex drive is a sham. In actuality, a woman's sex drive is weak, which gives them an enormous resistance in the copulative act to minimize energy loss. Yet, the belief that women desire sex as much as we do still persists. Why? Simply because their desires and feelings of various types are clothed in a sexual appearance and are expressed as such, which makes us confused. What is expressed under the guise of sexual desire is actually fear, greed, envy, competitiveness, sadness, vengeance, gratitude, pride, etc. If it were not so, females would be looking for us all the time, chasing us, and the situation would be reversed.

\par If you still doubt such an obvious truth, we can unmask and destroy the lie that victimized you with this observation: prostitutes and porn actresses will not offer their favors if they are not paid; the hottest foxes in schools, clubs, proms, and red-light areas do not offer themselves to shy, needy, faded, and broke males, but rather to swingers. Is there any objection remaining?

\par I will still crush and grind the rest of these lies a little bit more until they disappear altogether. In a research published by Marie Claire this month (July 2006), 76\% of interviewed women stated that they prefer to go shopping at the mall than to have an orgasm. I do not think the publisher has falsified the research... Who might have falsified it were the interviewees themselves. Liars as they are, I prioritize the suspicion that the remaining 24\% would also prefer to go shopping and did not tell the truth!

\par The climax of love stories are the boring kisses on the mouth and not the hot, wild sex.

\par People are reluctant in admitting that intercourse in and of itself is of little interest to females, because such a thought is unpleasant to both genders. Feminists then take the opportunity to say that we have repressed and castrated female sexuality, because the idea of them being inherently apathetic and cold displeases them.

\par Our naive opposers will say, \enquote{But why do women roar and get tripped on the sexual act, getting to the point of even losing sensitivity to pain?} The answer is this: because they are melodramatic, theatrical, and have the rare ability to believe in their own simulations and pretenses without losing the awareness that they are pretending. They accomplish such a feat by dividing themselves in two parts: one that believes their pretense and another that preserves the science of pretending. The excitement with an exclusively sexual appearance is, in actuality, much more of an emotional and passionate nature than exactly erotic. It is adrenaline elevated by an economic, sentimental, and social context without which sex will not happen. Femme fatal is a farce.

\par My opposers will say then that this is due to sexual repression imposed by men over women. This is a fallacy! Such a repression does not exist or, if it exists, it is imposed mainly by fathers and husbands, with the specific interest of centralizing female libido on one man only, and does not nullify the arousal attempts by most other human males. Let us do a test: let us put a woman in the midst of many men, preferably semi-undressed or with provocative clothes, and let us verify if they try to sexually repress her or encourage her... In fact, human males try more to encourage than to repress female sexuality, because they are thinking about mating all the time.

