\section{The privileges}

\par It is often said that females are poor victims of society, that they have been exploited and oppressed in all cultures since prehistory and that only in the 20th century they have managed to emancipate, that men are their enemies, etc. Let us unmask yet another lie.

\par All these studies that state that women have always been poor victims of males are exclusionary and biased. Exclusionary because they do not take into account the privileges that women have benefited from in the various eras. Biased because they do it on purpose. If we study the different societies, we will see that, actually, what happens is precisely the opposite, as Van Creveld points out. Men have always been intended for the worst, hardest, heaviest, and most dangerous tasks. In situations of danger, as in a natural disaster, men have a duty to protect women and children, and are, therefore, the last to receive security and life guarantees. Obviously, these rights of women and children are not wrong and are sacred. What is wrong is to lie by saying that we oppress and exploit them, when, actually, we were born to protect them. If we ceased to exist, as some feminists would like, who would step into the fire to rescue victims of a fire? Who would do the dangerous tasks in high towers and at the top of buildings? Who would walk through a current to rescue victims of a flood? Who would carry bags of cement and other heavy loads? Who would unload trucks? Who would kill oxen to send their meat to the butchery?

\par We flatter and fawn over females in hope of receiving crumbs of sex. The opposite has never happened. We compete vigorously against ourselves for them. Gangsters, famous men, and powerful men do not want fame, money, and power only to contemplate it... In a competition between males, which is socioeconomic, winners get the most desirable, beautiful, and perfect females, while losers have to content themselves with women whom the former men have rejected.

\par All of that favors females, and not us. We do not see women killing themselves for a space in the shade of our protection. After we have slaughtered ourselves, they simply wait and settle in the places that have been hierarchically reserved to them, along with the remaining men.

\par Females can make certain privileges that they themselves unceasingly provoke and seek look like a sad suffering, so that, based on this contrived appearance, they can claim more privileges. E.g. male polygamy (it is women themselves who are attracted to men who have many girlfriends), maternity, staying home while she is supported by a rich man, etc.

\par Privileges make them feel snobby and confident that they are desired. That is why they feel comfortable to abuse a man's feelings. Moreover, they continuously believe themselves chased and flirted with. It is enough that you stare at one of these privileged beings to be immediately seen as a chaser or a flirty guy. And if you are poor, black, or mixed, it is even worse. They never imagine that we are finding them uninteresting. Which is why we surprise and disconcert them when we ignore, avoid, and reject them.