\section{Mothers, wives, and daughters}

\par When talking to their male kids, many mothers do it as if they were mentally handicapped: they replace \enquote{R} with \enquote{L,} name everything in the diminutive, use a specific high-pitched tone of voice\footnotemark[14]. Besides, instead of giving tigers, sharks, crocodiles, dragons, and sword toys to their kids, they give them stuffed animals, teddy bears, rubber duckies, etc. so that they do not grow up.

\footnotetext[14]{In the first months of life, this behavior can be even necessary as a good way of establishing emotional affinity with the baby. But when it becomes an addiction and extends for many years, it becomes an obstacle that retards the development of masculinity. This is my opinion.}

\par As the poor boys grow older, the dependency for female affection grows with them. When they physically become adults, they are unable to live without the female affection and the presence of their mother or a replacement. When they fall in love, they transfer their \textbf{maternal imago} to their girlfriend or wife. This transference brings with it their expectations, obligations, and requirements. The poor boy expects from women what he used to expect from his mother: love. The boy in love pleases, obeys, gives gifts, and flatters, expecting to receive affection in return, because this worked when he was a kid. But the result now is nefarious. Females react in the opposite way to what he expects and disconcert him.

\par Devious as they are, women take advantage of this lack. Far from sympathizing with the emotional state of males, they use it as a tool to defend themselves and to dominate them.

\par To top it all off, devious women shout from the rooftops that the chosen ones are the sensitive, affectionate, romantic, good, honest, sincere, and laboring men. It is as if they said, \enquote{If you are good boys, we will give you love and sex the way you want it.} It is all a lie. Experience and direct observation reveals otherwise.

\par Before a beautiful woman, men submit themselves and do everything that they are told to, resembling dogs and beasts of burden. They give their all and receive the least in return. They expect to be rewarded with sex and affection of great quality, but they become frustrated.

\par Men in love, when they marry their goddesses, they get exploited, deceived, and betrayed. However, the thing started a long time ago...

\par Females learn how to dissimulate, to fool, to deceive, and to double-cross men since they are born. They are protected and taught by their mothers, even if these are not aware of it. They first exercise their art of deceit with their poor father: lying, circumventing his instructions and orders, dating in secret, etc. Once they are well trained, their ability will be employed on their boyfriends and later on their husbands. The dynamics is always the same: enjoying the pleasant sides of life while transferring the side effects and unpleasant consequences to someone else. Daughters want to freely do as they like while having the costs borne by their father. To date or promiscuously \enquote{pick up} men, girls demand that they be treated as an adult, but to cover the expenses and obligations of self-sustenance, they demand that they be treated as kids. Adult women want to live \enquote{freely,} free from any marital obligations, but without losing their rights of wife/girlfriend/fiance. Suckers have to bite the bullet so that devious women have fun.

\par Until they have learned to return consequences to other people's attitudes, the unfortunate males will suffer a lot at the hands of devious women.

\par He who does not transcend the notion of woman that originated from his maternal relationship will fall victim to passion. Inherent to assigning a maternal sense to a female animal is the assignment of a sacred sense to her, a fact that constitutes a profanity. And one does not cast pearls before swine with impunity.