\section{Why are they the opposite of what they confess}

\par The unconscious is in a relation of opposition and complement to the conscious psyche. This is one reason why people do not do what they say they will.

\par We do not get to know a person only by listening to what they say, we must observe them and check how they act and react in many situations. Moreover, there are also conscious inconsistencies done on purpose. Human beings, including females of the species, are pretending, fake, lying, deceiving, and hypocritical.

\par It is common for women to curse a man whom they are attracted to. Almost all women are unanimous in condemning the actions of jerks and playboys, denying up and down the possibility of desiring them, but when they are before these men, they faint and give themselves to them. All women assure that they desire good, working, and honest men, but when they stand before them, they consider them tiresome and boring.

\par This means that a man who tries to guide himself by what devious women say will be caught by surprise and will fare badly. Likewise, almost all interviews and polls that intend to demystify the disconcerting female [imagination] are ridiculous and fake, they only hinder and confuse our understanding.

\par Be very careful when you hear them saying, \textit{\enquote{I like men such and such, who do this or that.}} They will very likely be lying, because, in the field of love and sex, they are usually the opposite of what they confess.

\par Do not try to fit into their confessed, ideal masculine model. Note that they opt for the absurd. Men who \enquote{break their will} are precisely the opposite of what is proclaimed.

\par Do not waste your time by asking them what they want: observe them and you will figure out. If you ask, you will be deceived. It is not unusual for them to request precisely what they will reject when they receive it. They usually repay affection with indifference, and protective leadership with affection.

\par Understanding female psyche is essential to deal correctly with these delicious mermaids. However, true understanding comes from observation, not from conversations.

\par In school and college, we usually see them neglecting good, polite, and studious boys. They get together to admire and to competitively chase undisciplined, troublesome boys who prefer to drink, to do drugs, to have fun recklessly, and to avoid studying. Still, they deny, against all evidence, that they prefer the worst men when questioned. But impartial observation reveals that their selective criteria are the model of clothes, motorcycles, cars, and, depending on their age, the paycheck size, the bank account, and material goods. In short: social standing is all that matters to them.

\par Their preference for the worst men makes them naive and lets them get easily deceived by anyone. I know guys who rent motorcycles and cars to show them off outside of schools, bars, clubs, as if they owned them. They also often pay for beautiful prostitutes to escort them as if they were their girlfriends. The result comes swiftly, and quickly, many foolish women are taken to the love hotel. These unreasonable females do not resist the allure of false signs of power that may be convincing. Then, when they are abandoned after losing their virginity, they complain and curse every male on the Earth, as if they were not the ones responsible for having offered themselves to men whom they should not. And they keep lying shamelessly by saying that they are attracted to good and honest men.

\par As I read the other day, I do not remember where: women do not like a romantic dinner as they say, but rather the high-price whiskey, the diamond in the ring that they get as a gift, the gold of the jewelry... They use love to camouflage their shameful greed.

\par In spite of the lies that all women insist in trying to naively support, the truth is that female attraction is determined by male social value. If a man is seen as \enquote{the hot guy} or \enquote{the big shot} by the social circle of friends which \textbf{\underline{she}} is in, he will draw attention even if he is mediocre, stupid, childish, and promiscuous, as we can see in the movie \enquote{Kids.} He can have many girlfriends simultaneously, and all of them will find his promiscuity beautiful and will consider it a legitimate right. Thus, that which, under such conditions, women dare to call \enquote{love} is a piece of crap, a ridiculous sentimentality triggered by his social standing.

\par Most men are unable to seduce beautiful women simply because they believe that women are what they openly confess. By falling into these lying rabbit tricks, they act according to what they were induced to believe in, and get the opposite of the expected results. Meanwhile, the worst [...] do not care to lie and pretend to impress them and fool them without a qualm, and are rewarded with sex and affection of good quality. This keeps repeating itself everywhere, and, still, women never change. The irrational female passion is complicit with lies, addiction, and pretenses, while it rewards mediocrity and contributes to social degeneration\footnotemark[15].

\footnotetext[15]{}

\par Aim to see women as robots with intense feelings yet conditioned\footnotemark[16]. Female stance reflects masculine stance\footnotemark[17]. Change your behavior and women will change. Give them what they need, not what they ask or say that they want.

\footnotetext[16]{}
\footnotetext[17]{}

\par Try to be protective, leading, and caring, on the one hand, and simultaneously mysterious, distant, commanding, and cold, on the other hand. You will see that women lie when they swear that they prefer passionate, affectionate, lovey-dovey, warm, and needy men.

\par The opposition between what they say and what they actually feel is originated from the many confusion that disconcert the male gender. Let us see examples.

\par Women say that they like romantic men. This is partially true. They really like romantic and lovesick men for their slave, but they do not feel any sexual attraction for them. Women say that they hate and do not accept male infidelity. This is another partial truth. Indeed, the infidelity of an emotional slave is not accepted, but, curiously, the infidelity of inaccessible men (powerful men, famous men, and all socially-prominent men in general) is not only accepted, but it is also attractive. The number of women that an \enquote{outstanding} man has is, unfortunately, something that makes him interesting. Women spell out that they do not want to be dominated, but, when they date a democratic man, they get bored and consider him inactive, weak, and a \enquote{wimp,} because the poor man does not trample their opinions. Thus, we attest that almost everything that we hear from women about themselves is a lie.

\par Watch and you will attest that most promises that women make in love is not fulfilled: they promise to give you a call and do not call you, they promise to show up on dates and blow you off, they promise you a sex paradise and refuse it when the time comes, they promise fidelity and flirt with other guys, they promise to be understanding and call you \enquote{insecure} when you want a clarification on her suspicious behavior. They are dishonest in love and only keep what they promised when they fear the consequences of cheating. Therefore, when you receive a promise, do not believe that it will be kept willingly, and establish a \enquote{punishment} up to the fraud and inform her. If you do not do this, she will have fun while she fools you.

\par Do not get carried away by the charm of a siren's voice with her deceitful speech. If you waste your time by chasing the nonsense of what women say, they will refuse you their lively smile, their love-struck look, the scorching kisses, the warm hugs, and the mind-blowing sex. They will try to screw you in the end, because the logic that guides them is that of absolute sentimental selfishness. This is why it is lawful and fair that you do \enquote{arm} yourself and defend yourself. Always keep truth and reason on your side. Do not play dirty, leave that task to them.