\section{The value of silence}

\par A powerful and even coercive\footnotemark[19] counter-manipulative weapon is silence.

\footnotetext[19]{Note that, although I am informing the reader about the [...]}

\par In the same way as coldness, silence must not be used without discretion. If you think that by simply staying mute you will solve everything, you are wrong. You must use silence for long periods only when you have been a victim of any emotional malfeasance. The rest of the time, you must alleviate it with wise speeches. However, you must never be very talkative.

\par Simply keeping quiet will not solve anything. You must be quiet under certain conditions and alleviate silence under other conditions. Few can discern that; most men naively believe that generalizable, mechanically-polarized behaviors are effective.

\par Very few men are able to remain silent for long periods of conflict. Usually, we try to keep our mouth shut after we suffer an injustice, a subtle betrayal, or having our feelings turned into an object of irresponsible jokes, but we cannot stand it for too long. When we reach the edge of our tolerating capacity, we blow up and [...]

\par The will to say how we feel is something that eats us alive and corrodes us. It is worsened by the difficulty in verbalizing what we notice. This difficulty is due to the hellish confusing chaos of ideas and emotions that intertwine into an insane pandemonium purposefully induced by devious women, who keep themselves aware of everything that happens, at the same time they refuse us certainty, definition, and clarity so as to keep us confused. We have plenty of dissatisfaction, but as much as we try to define it and show it, we never feel it is enough.

\par This obsession comes from mental hyperactivity. If you stay outwardly quiet, but your mind still remains agitated inside, thinking thousands of foolishness, you will end up in a mental hospital. Silence is powerful and win women over, but it must come from the inside out, and never from the outside in. Keep your mind quiet in her presence. The moment you do not think, there will be no confusion or doubt, for there will be no thoughts about it. Her torturous provocations will have no effect. The disconcerting female behavior affects only men who waste their precious time thinking about it, in a foolish attempt to put her intentional puzzle together.

\par If you try to silence yourself from the outside to inside, you will develop psychosomatic diseases and will die. Only men who submit to inner spiritual discipline can attain true silence.

\par Try, if you are a victim of some sort of female malfeasance, to suddenly become silent for a long time. She will become silent and distant in return, but there will be a moment when she will not endure the torment and will try to get something out of you. This is where you must not say a thing and keep yourself quiet. I refer to a prolonged silence, and not a few hours one. This is very difficult. It requires full dispassion, a complete willingness to lose, detachment, iron discipline, and a will of steel.

\par As women are compulsive chatterboxes, we surpass them in the field of silence with relative ease if we stay disciplined. However, I say it again, we must be silent from the inside out.

\par Silence makes women desperate for not letting them know what is going on and what will happen. Once she reaches her resistance limit, she will try to get you into a argument, a [polemical discussion], or a fight\footnotemark[20]. Resist until you tire her out. Then the time has come to expose, in a straightforward, short and thick manner, your viewpoint and your requirements, withdrawing from the conversation before an argument is started.

\footnotetext[20]{Daniel Goleman says that the silence of a man who doesn't argue increases a woman's emotional stress.}

\par Females keep the understanding, the certainty, and the clear definition of what goes on in the relationship to themselves, but at the same time, they refuse them to a man in order to keep him stuck in confusion and doubt. They hide, by means of contradictory behaviors, the truth about what they feel, do, and plan, specially regarding their fidelity. Their undefined and inconsistent attitude is a weapon that disconcerts and renders the other powerless. However, through silence, we give this unwelcome burden back to them. Silence torments them for creating a situation where there is no definition for anything. In silence, there is no certainty and everything in undefined. Silence preserves mystery and does not let our intentions and feelings to be seen.

\par The maintenance of silence is difficult because we live in a mental culture in which thoughts are stimulated and seen as necessary. The belief that one must think and [...] one's head by over-thinking in order to solve life problems is very strong. The result is that we talk nonstop for having an hyperactive mind.

\par Silence must be broken by wise, protective, and slightly tender speeches when she behaves in an honest, transparent, and sincere manner (which seldom happens). There are, however, situations when silence is useless and even disrupting. These are situations that require the powerful emotional impact of a very wise speech.