\section{Shattering the little emotional hell}

\par You must have noticed that females are used to suddenly surprise us by disappearing or by not calling us back. They are used to promise and to not fulfill, to oscillate between approaching and distancing, to nourish our expectations and to thwart them, to suggest that they will call us and to not call, to purposefully provoke our wrath, to do precisely what we dislike or hate, etc. These are very well known little emotional hell that they deliberately and consciously raise. They do this to make our lives hell with doubt and to test us. They want to find out if we will become desperate, if we will seek them like crazy, etc.

\par A sudden disappearance is often preceded by indications and signals that allow us to detect it: sometimes silence, bad humor, or slightly disagreements, or, most of the time, misleading indicators that suggest the opposite of what is going to happen: too much affection, kindness, willingness, and goodwill. If your woman is being too nice, attentive, affectionate, etc., watch your back because you may be being set to receive the impact of a withdrawal syndrome caused by her sudden disappearance. When you notice that she is going to disappear, to stay without calling, or to purposefully not answer the phone in order to bother you, get ahead of her and steal the triumph from her by ordering her to not seek you, to not call your, and to wait indefinitely until you do it. This way, you disarm this little emotional game because you will have ordered her to do precisely what she was intending to. If this is very difficult for you, then do the opposite: get ahead by communicating a punitive decision that will heavily reverse the consequences of her sudden disappearance onto her.

\par As a general dominating rule, a sudden disappearance only happens after we have been \enquote{hooked.} A female disappears when she begins to suspect that you will be struck by her absence. Her intention is to cause you an ever-growing suffering in order to intensify your passion.