\centering \large{\textbf{About the author}}

\justifying \normalsize

\par The author of this book IS NEITHER A PSYCHOLOGIST NOR A MASTER of anyone. He STRICTLY REFUSES DISCIPLES and does not want followers of any kind. He simply exercises his right of thinking freely about lovesickness and wishes that people think by themselves. His ideas were published so that they could be discussed and improved by criticism, and are not intended for immature, dogmatic, or extremist people. This is neither a recipe book nor a manual!

\par The author REPROVES the formation of any doctrine groups based on his ideas, which he wishes to be a starting point for deeper reflections and other authors and viewpoints. He, for being a freethinker and real lover of continuous knowledge buildup, NOT ALWAYS AGREES WITH HIMSELF and considers that many of his ideas may be wrong! His ideas were published to be questioned and discussed, instead of being praised or depreciated. They are only another viewpoint among all the possible ones (perspectivism).

\par The author considers that all human beings have the right to do philosophy, that is, to think in a critical, deep, careful, and focused way. Anyone who claims to be his disciple is an IMPOSTOR!

\par There are no groups representing the ideas of this author in nowhere in the world, virtual or not. There are only groups with viewpoints similar to his in certain aspects.

\par People who are unable to continuously change their viewpoints should not mess with deep thoughts!